### 2012-05-14 report/paper.tex
Added latex of report

\documentclass[12pt]{article}
\setcounter{secnumdepth}{2}

\title{PubCrawl: A Paper Search Engine}
\author{Frank Li \\
Abhishek Sarkar \\
Manasi Vartak}
\date{May 16, 2012}

\usepackage{graphicx}

\begin{document}
\maketitle

\section{Introduction}

	A primary source of information for computer science researchers are published papers from conference proceedings and journals. However, there are simply too many papers in published in too many venues to keep track of. While experienced researchers are typically versed in the famous and influential papers of their respective fields, they may be less familiar with other areas that might still be needed for their work. Less experienced researchers and students may have even less or no knowledge of the relevant papers of a subject.

	To address this issue, we designed PubCrawl, a paper search engine. Using this system allows researchers to query for the most important and relevant papers in a field, particularly one they are not familiar with. PubCrawl uses Apache Lucene for text indexing to measure a paper’s relevance to a query, and an adaptation of PageRank on the papers citation graph for weighting a paper’s importance. Currently all papers in the Association of Computing Machinery (ACM) Digital Library database have been processed. A simple web user interface is provided, where users can input queries and weights for what attributes they feel is most important, to tune the result rankings to fit what they feel is most appropriate. The top papers are returned, with hyperlinks to the papers’ ACM homepage.

	In this report, we detail the design of PubCrawl and investigate the effects of many of its features. We conduct a user study to compare the performance of our ranking system versus other current systems.

\section{Related Work}

There are a few paper search engines currently in existence: CiteseerX, Google Scholar, and Microsoft Academic Search.

CiteseerX's data set is scraped from the web by a crawler, and processed in an automated fashion. This has provided CiteseerX with wide and largely hands-off coverage of papers. However, due to the purely automated approach used and the heterogeneity in data representation on the web, the data collected contains errors and missing information. For example, the crawler has mistaken the wrong string for the title of a number of papers.

\section{PubCrawl Design}

PubCrawl is designed to rank papers based on relevance and importance. To measure relevance, we use Apache Lucene, a high-performance text search engine library for Java. Lucene is used to provide text indexing, returning the papers most textually relevant to a query. To measure importance, we use a variation of the classic PageRank algorithm on the citation graph of papers. The weighting between the text indexing and PageRank score is an input the users can provide, as discussed in \ref{sec:implementation}. Currently, the ACM dataset has been gathered and applied using PubCrawl.

\subsection{Lucene Text Indexing}
%Abhishek

\subsection{Adapted PageRank}
\label{sec:pagerank}

The relationship between academic papers draws a strong analogy with that between web pages. Just as pages on the web embed links to other pages, papers cite other papers. This forms a directed graph of paper nodes and citation edges, where an edge from one paper $A$ to another paper $B$ indicates that $A$ cited $B$.

To exploit the similarity between the two environments, we use a variation of the PageRank algorithm. PageRank is an algorithm used by the Google search engine that provides a weighted score for web pages based on the number of external pages that cite a particular web page, and the PageRank of those external pages. We use a similar framework for academic papers, where a paper's score is based on the number of other papers citing it, and the score of those papers. The most simple form of this captured by the following equation:\\
\begin{equation}
\label{eqn:basic}
S(p)= \Sigma_{c \in C} \frac{S(c)}{D(c)}
\end{equation}
where $p$ is the paper being scored, $C$ is the set of all papers that cite $p$, $S$ is the scoring function, and $D$ is the degree function (indicating the number of papers a certain paper cites).

The score of all nodes can be calculated in an iterative manner. All nodes can be initialized to a default score, such as 1. Then, in each round, Equation \ref{eqn:basic} can be applied to all nodes. This process is repeated until node scores converge. However, this scoring function is further complicated by a couple of features of academic paper relations: cycles and components.

Citation cycles provide one source of complication. In citation cycles, a paper's chain of citations returns to the paper itself. A number of these cycles exist in the data set. In general, these cycles act as a score sink, shifting the score of external nodes into the cycle round after round. Inside the cycle, the score rotates among nodes, preventing convergence. To reduce the impact of these cycles, a score source is provided for node each round, as also done in PageRank. To provide convergence, the total sum of all node scores must remain constant, so node scores must be normalized per round. This results in an updated scoring function of:\\
\begin{equation}
\label{eqn:cycle}
S(p)= n(\Sigma_{c \in C} \frac{S(c)}{D(c)}+E(p))
\end{equation}
where $E$ is a source of score, $n$ is the normalization factor, and all other variables remain as defined.

Components in the citation graph are the other source of complication. Papers in the same component are either both part of the same citation chain or share a common ancestor or descendant in their respective chain. The ACM data exhibits a large number (???? exact number????) of components, with a small number of large components and a large number of components with just a few papers (Figure ???). Small components are papers that don't cite any other papers in the data set and aren't heavily cited. This implies that nodes in small components should not be highly ranked. 
To adjust for this, nodes are categorized into the components they belong in. Instead of initializing node scores to be a constant value such as 1, they are instead initialized to a score linear to the size of the component containing the nodes. Intuitively, this means that papers in larger components will receive higher scores, as desired.

A final variation on the basic scoring function is the incorporation of a damping factor $d$. A user following a citation chain will eventually stop, possibly at the end of the chain. Intuitively, the farther down a chain a user traverses, the less likely the papers will relevant and important to the original query, and the more likely the user will stop. The damping factor models this behaviour by reducing the change produced by the scoring function as the number of rounds increases. Adapted from PageRank, this results in the final version of our scoring function:\\
\begin{equation}
\label{eqn:damping}
S(p)= n(\frac{1-d}{N}+d(\Sigma_{c \in C} \frac{S(c)}{D(c)}+E(p)))
\end{equation}
where $d$ is the damping factor, $N$ is the total number of papers/nodes in the network, and all other variables remain as defined.

\section{Implementation}
\label{sec:implementation}

MANASI'S WEBSITE STUFF//
%Manasi's website stuff

For PubCrawl's implementation of the adapted PageRank scoring function, we used several parameters for variables defined in Section \ref{sec:pagerank}:\\

\begin{itemize}
\item For the score source $E$, we use a uniform value. We minimize the value of $E$ that still results in convergence, to reduce the total amount of freely created score.

\item For initializing node scores, we use a linear relationship with the size of the component containing the node. If the total number of papers (and nodes) is $N$ and paper $p$ is in a component with $X$ nodes, then the initial score for $p$ is set to $\frac{X}{N}$. Thus, larger components start with initially higher scores, and typically converge with higher final scores.

\item For the damping factor of our final scoring function (Equation \ref{eqn:damping}), we use $d=0.85$. This is a reflection of the PageRank study indicating this value as reasonable, rather than a precisely chosen one.

\end{itemize}

\section{User Study}

\section{Results}

\section{Conclusion}

\section{Acknowledgements}
\null

\end{document}

### 2012-05-15 report/paper.tex
Added emails :)

@@
 \documentclass[12pt]{article}
+\usepackage[letterpaper,margin=1in]{geometry}
+\usepackage{graphicx}
+
 \setcounter{secnumdepth}{2}
@@
 \title{PubCrawl: A Paper Search Engine}
-\author{Frank Li \\
-Abhishek Sarkar \\
-Manasi Vartak}
+\author{Frank Li (frankli@mit.edu)\\
+Abhishek Sarkar (aksarkar@mit.edu)\\
+Manasi Vartak (mvartak@mit.edu)}
 \date{May 16, 2012}
-
-\usepackage{graphicx}
 
@@
 
-	A primary source of information for computer science researchers are published papers from conference proceedings and journals.
-However, there are simply too many papers in published in too many venues to keep track of.
-While experienced researchers are typically versed in the famous and influential papers of their respective fields, they may be less familiar with other areas that might still be needed for their work.
-Less experienced researchers and students may have even less or no knowledge of the relevant papers of a subject.
+A primary source of information for computer science researchers are published
+papers from conference proceedings and journals. However, there are simply too
+many papers in published in too many venues to keep track of. While experienced
+researchers are typically versed in the famous and influential papers of their
+respective fields, they may be less familiar with other areas that might still
+be needed for their work. Less experienced researchers and students may have
+even less or no knowledge of the relevant papers of a subject.
 
-	To address this issue, we designed PubCrawl, a paper search engine.
-Using this system allows researchers to query for the most important and relevant papers in a field, particularly one they are not familiar with.
-PubCrawl uses Apache Lucene for text indexing to measure a paper’s relevance to a query, and an adaptation of PageRank on the papers citation graph for weighting a paper’s importance.
-Currently all papers in the Association of Computing Machinery (ACM) Digital Library database have been processed.
-A simple web user interface is provided, where users can input queries and weights for what attributes they feel is most important, to tune the result rankings to fit what they feel is most appropriate.
-The top papers are returned, with hyperlinks to the papers’ ACM homepage.
+To address this issue, we designed PubCrawl, a paper search engine. Using this
+system allows researchers to query for the most important and relevant papers
+in a field, particularly one they are not familiar with. PubCrawl uses Apache
+Lucene for text indexing to measure a paper’s relevance to a query, and an
+adaptation of PageRank on the papers citation graph for weighting a paper’s
+importance. Currently all papers in the Association of Computing Machinery
+(ACM) Digital Library database have been processed. A simple web user interface
+is provided, where users can input queries and weights for what attributes they
+feel is most important, to tune the result rankings to fit what they feel is
+most appropriate. The top papers are returned, with hyperlinks to the papers’
+ACM homepage.
 
-	In this report, we detail the design of PubCrawl and investigate the effects of many of its features.
-We conduct a user study to compare the performance of our ranking system versus other current systems.
+In this report, we detail the design of PubCrawl and investigate the effects of
+many of its features. We conduct a user study to compare the performance of our
+ranking system versus other current systems.
 
@@
 
-There are a few paper search engines currently in existence: CiteseerX, Google Scholar, and Microsoft Academic Search.
+There are a few paper search engines currently in existence: CiteseerX, Google
+Scholar, and Microsoft Academic Search.
 
-CiteseerX's data set is scraped from the web by a crawler, and processed in an automated fashion.
-This has provided CiteseerX with wide and largely hands-off coverage of papers.
-However, due to the purely automated approach used and the heterogeneity in data representation on the web, the data collected contains errors and missing information.
-For example, the crawler has mistaken the wrong string for the title of a number of papers.
+CiteseerX's data set is scraped from the web by a crawler, and processed in an
+automated fashion. This has provided CiteseerX with wide and largely hands-off
+coverage of papers. However, due to the purely automated approach used and the
+heterogeneity in data representation on the web, the data collected contains
+errors and missing information. For example, the crawler has mistaken the wrong
+string for the title of a number of papers.
 
@@
 
-PubCrawl is designed to rank papers based on relevance and importance.
-To measure relevance, we use Apache Lucene, a high-performance text search engine library for Java.
-Lucene is used to provide text indexing, returning the papers most textually relevant to a query.
-To measure importance, we use a variation of the classic PageRank algorithm on the citation graph of papers.
-The weighting between the text indexing and PageRank score is an input the users can provide, as discussed in \ref{sec:implementation}.
-Currently, the ACM dataset has been gathered and applied using PubCrawl.
+PubCrawl is designed to rank papers based on relevance and importance. To
+measure relevance, we use Apache Lucene, a high-performance text search engine
+library for Java. Lucene is used to provide text indexing, returning the papers
+most textually relevant to a query. To measure importance, we use a variation
+of the classic PageRank algorithm on the citation graph of papers. The
+weighting between the text indexing and PageRank score is an input the users
+can provide, as discussed in \ref{sec:implementation}. Currently, the ACM
+dataset has been gathered and applied using PubCrawl.
 
@@
 
-The relationship between academic papers draws a strong analogy with that between web pages.
-Just as pages on the web embed links to other pages, papers cite other papers.
-This forms a directed graph of paper nodes and citation edges, where an edge from one paper $A$ to another paper $B$ indicates that $A$ cited $B$.
+The relationship between academic papers draws a strong analogy with that
+between web pages. Just as pages on the web embed links to other pages, papers
+cite other papers. This forms a directed graph of paper nodes and citation
+edges, where an edge from one paper $A$ to another paper $B$ indicates that $A$
+cited $B$.
 
-To exploit the similarity between the two environments, we use a variation of the PageRank algorithm.
-PageRank is an algorithm used by the Google search engine that provides a weighted score for web pages based on the number of external pages that cite a particular web page, and the PageRank of those external pages.
-We use a similar framework for academic papers, where a paper's score is based on the number of other papers citing it, and the score of those papers.
-The most simple form of this captured by the following equation:\\
+To exploit the similarity between the two environments, we use a variation of
+the PageRank algorithm. PageRank is an algorithm used by the Google search
+engine that provides a weighted score for web pages based on the number of
+external pages that cite a particular web page, and the PageRank of those
+external pages. We use a similar framework for academic papers, where a paper's
+score is based on the number of other papers citing it, and the score of those
+papers. The most simple form of this captured by the following equation:\\
 \begin{equation}
@@
 \end{equation}
-where $p$ is the paper being scored, $C$ is the set of all papers that cite $p$, $S$ is the scoring function, and $D$ is the degree function (indicating the number of papers a certain paper cites).
+where $p$ is the paper being scored, $C$ is the set of all papers that cite
+$p$, $S$ is the scoring function, and $D$ is the degree function (indicating
+the number of papers a certain paper cites).
 
-The score of all nodes can be calculated in an iterative manner.
-All nodes can be initialized to a default score, such as 1.
-Then, in each round, Equation \ref{eqn:basic} can be applied to all nodes.
-This process is repeated until node scores converge.
-However, this scoring function is further complicated by a couple of features of academic paper relations: cycles and components.
+The score of all nodes can be calculated in an iterative manner. All nodes can
+be initialized to a default score, such as 1. Then, in each round, Equation
+\ref{eqn:basic} can be applied to all nodes. This process is repeated until
+node scores converge. However, this scoring function is further complicated by
+a couple of features of academic paper relations: cycles and components.
 
-Citation cycles provide one source of complication.
-In citation cycles, a paper's chain of citations returns to the paper itself.
-A number of these cycles exist in the data set.
-In general, these cycles act as a score sink, shifting the score of external nodes into the cycle round after round.
-Inside the cycle, the score rotates among nodes, preventing convergence.
-To reduce the impact of these cycles, a score source is provided for node each round, as also done in PageRank.
-To provide convergence, the total sum of all node scores must remain constant, so node scores must be normalized per round.
-This results in an updated scoring function of:\\
+Citation cycles provide one source of complication. In citation cycles, a
+paper's chain of citations returns to the paper itself. A number of these
+cycles exist in the data set. In general, these cycles act as a score sink,
+shifting the score of external nodes into the cycle round after round. Inside
+the cycle, the score rotates among nodes, preventing convergence. To reduce the
+impact of these cycles, a score source is provided for node each round, as also
+done in PageRank. To provide convergence, the total sum of all node scores must
+remain constant, so node scores must be normalized per round. This results in
+an updated scoring function of:\\
 \begin{equation}
@@
 \end{equation}
-where $E$ is a source of score, $n$ is the normalization factor, and all other variables remain as defined.
+where $E$ is a source of score, $n$ is the normalization factor, and all other
+variables remain as defined.
 
-Components in the citation graph are the other source of complication.
-Papers in the same component are either both part of the same citation chain or share a common ancestor or descendant in their respective chain.
-The ACM data exhibits a large number (????
-exact number????) of components, with a small number of large components and a large number of components with just a few papers (Figure ???).
-Small components are papers that don't cite any other papers in the data set and aren't heavily cited.
-This implies that nodes in small components should not be highly ranked.
-To adjust for this, nodes are categorized into the components they belong in.
-Instead of initializing node scores to be a constant value such as 1, they are instead initialized to a score linear to the size of the component containing the nodes.
-Intuitively, this means that papers in larger components will receive higher scores, as desired.
+Components in the citation graph are the other source of complication. Papers
+in the same component are either both part of the same citation chain or share
+a common ancestor or descendant in their respective chain. The ACM data
+exhibits a large number (???? exact number????) of components, with a small
+number of large components and a large number of components with just a few
+papers (Figure ???). Small components are papers that don't cite any other
+papers in the data set and aren't heavily cited. This implies that nodes in
+small components should not be highly ranked. To adjust for this, nodes are
+categorized into the components they belong in. Instead of initializing node
+scores to be a constant value such as 1, they are instead initialized to a
+score linear to the size of the component containing the nodes. Intuitively,
+this means that papers in larger components will receive higher scores, as
+desired.
 
-A final variation on the basic scoring function is the incorporation of a damping factor $d$.
-A user following a citation chain will eventually stop, possibly at the end of the chain.
-Intuitively, the farther down a chain a user traverses, the less likely the papers will relevant and important to the original query, and the more likely the user will stop.
-The damping factor models this behaviour by reducing the change produced by the scoring function as the number of rounds increases.
-Adapted from PageRank, this results in the final version of our scoring function:\\
+A final variation on the basic scoring function is the incorporation of a
+damping factor $d$. A user following a citation chain will eventually stop,
+possibly at the end of the chain. Intuitively, the farther down a chain a user
+traverses, the less likely the papers will relevant and important to the
+original query, and the more likely the user will stop. The damping factor
+models this behaviour by reducing the change produced by the scoring function
+as the number of rounds increases. Adapted from PageRank, this results in the
+final version of our scoring function:\\
+
 \begin{equation}
@@
 \end{equation}
-where $d$ is the damping factor, $N$ is the total number of papers/nodes in the network, and all other variables remain as defined.
+
+where $d$ is the damping factor, $N$ is the total number of papers/nodes in the
+network, and all other variables remain as defined.
 
@@
 
-MANASI'S WEBSITE STUFF//
 %Manasi's website stuff
 
-For PubCrawl's implementation of the adapted PageRank scoring function, we used several parameters for variables defined in Section \ref{sec:pagerank}:\\
+For PubCrawl's implementation of the adapted PageRank scoring function, we used
+several parameters for variables defined in Section \ref{sec:pagerank}:\\
 
 \begin{itemize}
-\item For the score source $E$, we use a uniform value. We minimize the value of $E$ that still results in convergence, to reduce the total amount of freely created score.
+\item For the score source $E$, we use a uniform value. We minimize the value
+  of $E$ that still results in convergence, to reduce the total amount of
+  freely created score.
 
-\item For initializing node scores, we use a linear relationship with the size of the component containing the node.
-If the total number of papers (and nodes) is $N$ and paper $p$ is in a component with $X$ nodes, then the initial score for $p$ is set to $\frac{X}{N}$.
-Thus, larger components start with initially higher scores, and typically converge with higher final scores.
+\item For initializing node scores, we use a linear relationship with the size
+  of the component containing the node. If the total number of papers (and
+  nodes) is $N$ and paper $p$ is in a component with $X$ nodes, then the
+  initial score for $p$ is set to $\frac{X}{N}$. Thus, larger components start
+  with initially higher scores, and typically converge with higher final
+  scores.
 
-\item For the damping factor of our final scoring function (Equation \ref{eqn:damping}), we use $d=0.85$.
-This is a reflection of the PageRank study indicating this value as reasonable, rather than a precisely chosen one.
+\item For the damping factor of our final scoring function (Equation
+  \ref{eqn:damping}), we use $d=0.85$. This is a reflection of the PageRank
+  study indicating this value as reasonable, rather than a precisely chosen
+  one.
 
@@
 
-\section{Acknowledgements}
+\section{Acknowledgments}
 \null

### 2012-05-15 report/paper.tex
Add abstract

--- 2012-05-14 report/paper.tex
@@
 \title{PubCrawl: A Paper Search Engine}
-\author{Frank Li \\
-Abhishek Sarkar \\
-Manasi Vartak}
+\author{Frank Li (frankli@mit.edu) \\
+Abhishek Sarkar (aksarkar@mit.edu)\\
+Manasi Vartak (mvartak@mit.edu)}
 \date{May 16, 2012}
@@
 \maketitle
+
+\begin{abstract}
+Searching for documents ranked by relevance is a well-studied problem for web
+pages. In particular, there are frameworks for estimating relevance as a
+function of the content of the document and algorithms for estimating relevance
+as a function of incoming links. However, further specialization of these
+techniques is required to search a corpus of academic papers. Academic papers
+are highly structured, lending additional weight to matches which appear in
+important sections such as the title or abstract. Moreover, citations have
+contextual information which changes the weight which should be contributed to
+cited papers. Here we describe PubCrawl, a search engine built for the ACM
+Digital Library. The system allows users to weight the relative importance of
+matches in the title, abstract, full text, and the PageRank of each hit,
+providing a platform to test further refinements of the algorithms. We evaluate
+the system in user studies.
+\end{abstract}
 
@@
 
-	To address this issue, we designed PubCrawl, a paper search engine.
-Using this system allows researchers to query for the most important and relevant papers in a field, particularly one they are not familiar with.
-PubCrawl uses Apache Lucene for text indexing to measure a paper’s relevance to a query, and an adaptation of PageRank on the papers citation graph for weighting a paper’s importance.
+	To address this issue, researchers have create paper search engines, such as Google Scholar and CiteseerX.
+However, the ranking process for these systems is largely privately maintained.
+In this paper, we investigate the process of ranking in the academic papers setting.
+An understanding of this is important to create a better search system.
+
+	To do this, we designed PubCrawl, a paper search engine, as a testing bed for ranking mechanisms.
+In building PubCrawl, we used Apache Lucene for text indexing to measure a paper’s relevance to a query, and an adaptation of PageRank on the papers citation graph for weighting a paper’s importance.
 Currently all papers in the Association of Computing Machinery (ACM) Digital Library database have been processed.
@@
 
-There are a few paper search engines currently in existence: CiteseerX, Google Scholar, and Microsoft Academic Search.
+There are a few paper search engines currently in existence, such as CiteseerX and Google Scholar.
+Their ranking process is largely maintained privately, but several characteristics of both are described in this section.
 
@@
 For example, the crawler has mistaken the wrong string for the title of a number of papers.
+This leads to some errors in the processing of both the paper data and queries.
+
+Google Scholar also operates with a crawler, and exhibits some of the same dirty data issues as CiteseerX.
+Additionally, Google Scholar has been shown to be heavily influenced by citation count, which may be inappropriate for some user queries.
 
@@
 Currently, the ACM dataset has been gathered and applied using PubCrawl.
+Through the design of the system, we discuss the effect of a number of its features.
 
@@
 
+\begin{figure}[t]
+\centering
+	\includegraphics[width=5in]{images/component-graph}
+	\caption{Sizes of components in the ACM data set and the number of each size's occurrence.}	
+	\label{comp-size}
+\end{figure}
+
 Components in the citation graph are the other source of complication.
 Papers in the same component are either both part of the same citation chain or share a common ancestor or descendant in their respective chain.
-The ACM data exhibits a large number (????
-exact number????) of components, with a small number of large components and a large number of components with just a few papers (Figure ???).
-Small components are papers that don't cite any other papers in the data set and aren't heavily cited.
+The ACM data exhibits 45,571 total components, with one large component of 176,285 papers, and a large number of smaller components ranging in size from one to ten papers, as displayed in Figure \ref{comp-size}.
+Small components are papers that don't cite many or any other papers in the data set and aren't heavily cited.
 This implies that nodes in small components should not be highly ranked.
+
 To adjust for this, nodes are categorized into the components they belong in.
@@
 \begin{itemize}
-\item For the score source $E$, we use a uniform value. We minimize the value of $E$ that still results in convergence, to reduce the total amount of freely created score.
+\item For the score source $E$, we use a uniform value.
+We minimize the value of $E$ that still results in convergence, to reduce the total amount of freely created score.
+In our system, we found $E=0.1$ to be appropriate.
 

### 2012-05-15 index/Searcher.java
Extend example to search multiple fields with variable boosting

@@ -7,20 +7,28 @@ import org.apache.lucene.document.*;
 import org.apache.lucene.index.*;
 import org.apache.lucene.queryParser.*;
 import org.apache.lucene.search.*;
+import org.apache.lucene.search.function.*;
 import org.apache.lucene.store.*;
 import org.apache.lucene.util.*;
 
 class Searcher {
   public static void main(String[] args) {
-    if (args.length < 1) {
-      System.err.println("Usage: java Searcher INDEX");
+    if (args.length < 4) {
+      System.err.println("Usage: java Searcher INDEX TWEIGHT AWEIGHT FWEIGHT");
       System.exit(1);
     }
     try {
       IndexReader r = IndexReader.open(FSDirectory.open(new File(args[0])));
       IndexSearcher s = new IndexSearcher(r);
       Analyzer a = new StandardAnalyzer(Version.LUCENE_36);
-      QueryParser p = new QueryParser(Version.LUCENE_36, "fulltext", a);
+      String[] fields = new String[] {"title", "abstract", "fulltext"};
+      Map<String, Float> boosts = new HashMap<String, Float>();
+      boosts.put("title", Float.parseFloat(args[1]));
+      boosts.put("abstract", Float.parseFloat(args[2]));
+      boosts.put("fulltext", Float.parseFloat(args[3]));
+      QueryParser p = new MultiFieldQueryParser(Version.LUCENE_36, fields, a,
+                                                boosts);
+      ValueSourceQuery pagerank = new FieldScoreQuery("pagerank", FieldScoreQuery.Type.FLOAT);
       Scanner in = new Scanner(System.in);
       while (in.hasNextLine()) {
         Query q = p.parse(in.nextLine().trim());

### 2012-05-15 report/paper.tex
Added color/pic to presentation, expanded report

@@
 \maketitle
-
-\begin{abstract}
-Searching for documents ranked by relevance is a well-studied problem for web
-pages. In particular, there are frameworks for estimating relevance as a
-function of the content of the document and algorithms for estimating relevance
-as a function of incoming links. However, further specialization of these
-techniques is required to search a corpus of academic papers. Academic papers
-are highly structured, lending additional weight to matches which appear in
-important sections such as the title or abstract. Moreover, citations have
-contextual information which changes the weight which should be contributed to
-cited papers. Here we describe PubCrawl, a search engine built for the ACM
-Digital Library. The system allows users to weight the relative importance of
-matches in the title, abstract, full text, and the PageRank of each hit,
-providing a platform to test further refinements of the algorithms. We evaluate
-the system in user studies.
-\end{abstract}
 
@@
 
-\begin{figure}[t]
-\centering
-	\includegraphics[width=5in]{images/component-graph}
-	\caption{Sizes of components in the ACM data set and the number of each size's occurrence.}	
-	\label{comp-size}
-\end{figure}
-
 Components in the citation graph are the other source of complication.
 Papers in the same component are either both part of the same citation chain or share a common ancestor or descendant in their respective chain.
-The ACM data exhibits 45,571 total components, with one large component of 176,285 papers, and a large number of smaller components ranging in size from one to ten papers, as displayed in Figure \ref{comp-size}.
-Small components are papers that don't cite many or any other papers in the data set and aren't heavily cited.
+The ACM data exhibits a large number (????
+exact number????) of components, with a small number of large components and a large number of components with just a few papers (Figure ???).
+Small components are papers that don't cite any other papers in the data set and aren't heavily cited.
 This implies that nodes in small components should not be highly ranked.
-
 To adjust for this, nodes are categorized into the components they belong in.

### 2012-05-15 pagerank.py
Added component summary code

@@ -9,7 +9,6 @@ from sets import Set
 
 rounds=0
 
-
 # Try to connect
 conn=psycopg2.connect("dbname='' user='' password='' host='localhost' port=5433")
 cur = conn.cursor()
@@ -101,7 +100,19 @@ print "Citations componentized at ", (time()-start)/60
 
 print "Beginning component check"
 			
-#Check
+size_dict = {}
+
+#determine sizes of components
+for comp in comp_list:
+	tmp_size = len(comp)
+	if tmp_size in size_dict:
+		size_dict[tmp_size]+=1
+	else:
+		size_dict[tmp_size]=1
+
+#print out sizes of components
+for k in size_dict:
+	print k, size_dict[k]
 
 pr_total = 0.0
 ctr = 0

### 2012-05-15 report/paper.tex
Fix LaTeX formatting again
Fix typos

--- 2012-05-15 report/paper.tex
@@
 \title{PubCrawl: A Paper Search Engine}
-\author{Frank Li (frankli@mit.edu) \\
+\author{Frank Li (frankli@mit.edu)\\
 Abhishek Sarkar (aksarkar@mit.edu)\\
@@
 
-	A primary source of information for computer science researchers are published papers from conference proceedings and journals.
-However, there are simply too many papers in published in too many venues to keep track of.
-While experienced researchers are typically versed in the famous and influential papers of their respective fields, they may be less familiar with other areas that might still be needed for their work.
-Less experienced researchers and students may have even less or no knowledge of the relevant papers of a subject.
+A primary source of information for computer science researchers are published
+papers from conference proceedings and journals. However, there are simply too
+many papers in published in too many venues to keep track of. While experienced
+researchers are typically versed in the famous and influential papers of their
+respective fields, they may be less familiar with other areas that might still
+be needed for their work. Less experienced researchers and students may have
+even less or no knowledge of the relevant papers of a subject.
 
-	To address this issue, researchers have create paper search engines, such as Google Scholar and CiteseerX.
-However, the ranking process for these systems is largely privately maintained.
-In this paper, we investigate the process of ranking in the academic papers setting.
-An understanding of this is important to create a better search system.
+To address this issue, researchers have create paper search engines, such as
+Google Scholar and CiteseerX. However, the ranking process for these systems is
+largely privately maintained. In this paper, we investigate the process of
+ranking in the academic papers setting. An understanding of this is important
+to create a better search system.
 
-	To do this, we designed PubCrawl, a paper search engine, as a testing bed for ranking mechanisms.
-In building PubCrawl, we used Apache Lucene for text indexing to measure a paper’s relevance to a query, and an adaptation of PageRank on the papers citation graph for weighting a paper’s importance.
-Currently all papers in the Association of Computing Machinery (ACM) Digital Library database have been processed.
-A simple web user interface is provided, where users can input queries and weights for what attributes they feel is most important, to tune the result rankings to fit what they feel is most appropriate.
-The top papers are returned, with hyperlinks to the papers’ ACM homepage.
+To do this, we designed PubCrawl, a paper search engine, as a testing bed for
+ranking mechanisms. In building PubCrawl, we used Apache Lucene for text
+indexing to measure a paper’s relevance to a query, and an adaptation of
+PageRank on the papers citation graph for weighting a paper’s importance.
+Currently all papers in the Association of Computing Machinery (ACM) Digital
+Library database have been processed. A simple web user interface is provided,
+where users can input queries and weights for what attributes they feel is most
+important, to tune the result rankings to fit what they feel is most
+appropriate. The top papers are returned, with hyperlinks to the papers’ ACM
+homepage.
 
-	In this report, we detail the design of PubCrawl and investigate the effects of many of its features.
-We conduct a user study to compare the performance of our ranking system versus other current systems.
+In this report, we detail the design of PubCrawl and investigate the effects of
+many of its features. We conduct a user study to compare the performance of our
+ranking system versus other current systems.
 
@@
 
-There are a few paper search engines currently in existence, such as CiteseerX and Google Scholar.
-Their ranking process is largely maintained privately, but several characteristics of both are described in this section.
+There are a few paper search engines currently in existence, such as CiteseerX
+and Google Scholar. Their ranking process is largely maintained privately, but
+several characteristics of both are described in this section.
 
-CiteseerX's data set is scraped from the web by a crawler, and processed in an automated fashion.
-This has provided CiteseerX with wide and largely hands-off coverage of papers.
-However, due to the purely automated approach used and the heterogeneity in data representation on the web, the data collected contains errors and missing information.
-For example, the crawler has mistaken the wrong string for the title of a number of papers.
-This leads to some errors in the processing of both the paper data and queries.
+CiteseerX's data set is scraped from the web by a crawler, and processed in an
+automated fashion. This has provided CiteseerX with wide and largely hands-off
+coverage of papers. However, due to the purely automated approach used and the
+heterogeneity in data representation on the web, the data collected contains
+errors and missing information. For example, the crawler has mistaken the wrong
+string for the title of a number of papers. This leads to some errors in the
+processing of both the paper data and queries.
 
-Google Scholar also operates with a crawler, and exhibits some of the same dirty data issues as CiteseerX.
-Additionally, Google Scholar has been shown to be heavily influenced by citation count, which may be inappropriate for some user queries.
+Google Scholar also operates with a crawler, and exhibits some of the same
+dirty data issues as CiteseerX. Additionally, Google Scholar has been shown to
+be heavily influenced by citation count, which may be inappropriate for some
+user queries.
 
@@
 
-PubCrawl is designed to rank papers based on relevance and importance.
-To measure relevance, we use Apache Lucene, a high-performance text search engine library for Java.
-Lucene is used to provide text indexing, returning the papers most textually relevant to a query.
-To measure importance, we use a variation of the classic PageRank algorithm on the citation graph of papers.
-The weighting between the text indexing and PageRank score is an input the users can provide, as discussed in \ref{sec:implementation}.
-Currently, the ACM dataset has been gathered and applied using PubCrawl.
-Through the design of the system, we discuss the effect of a number of its features.
+PubCrawl is designed to rank papers based on relevance and importance. To
+measure relevance, we use Apache Lucene, a high-performance text search engine
+library for Java. Lucene is used to provide text indexing, returning the papers
+most textually relevant to a query. To measure importance, we use a variation
+of the classic PageRank algorithm on the citation graph of papers. The
+weighting between the text indexing and PageRank score is an input the users
+can provide, as discussed in \ref{sec:implementation}. Currently, the ACM
+dataset has been gathered and applied using PubCrawl. Through the design of the
+system, we discuss the effect of a number of its features.
 
@@
 \end{equation}
-where $E$ is a source of score, $n$ is the normalization factor, and all other variables remain as defined.
+where $E$ is a source of score, $n$ is the normalization factor, and all other
+variables remain as defined.
 
 \begin{figure}[t]
-\centering
-	\includegraphics[width=5in]{images/component-graph}
-	\caption{Sizes of components in the ACM data set and the number of each size's occurrence.}	
+\centering \includegraphics[width=5in]{images/component-graph}
+	\caption{Sizes of components in the ACM data set and the number of each
+      size's occurrence.}
 	\label{comp-size}
@@
 
-Components in the citation graph are the other source of complication.
-Papers in the same component are either both part of the same citation chain or share a common ancestor or descendant in their respective chain.
-The ACM data exhibits 45,571 total components, with one large component of 176,285 papers, and a large number of smaller components ranging in size from one to ten papers, as displayed in Figure \ref{comp-size}.
-Small components are papers that don't cite many or any other papers in the data set and aren't heavily cited.
-This implies that nodes in small components should not be highly ranked.
+Components in the citation graph are the other source of complication. Papers
+in the same component are either both part of the same citation chain or share
+a common ancestor or descendant in their respective chain. The ACM data
+exhibits 45,571 total components, with one large component of 176,285 papers,
+and a large number of smaller components ranging in size from one to ten
+papers, as displayed in Figure \ref{comp-size}. Small components are papers
+that don't cite many or any other papers in the data set and aren't heavily
+cited. This implies that nodes in small components should not be highly ranked.
 
 To adjust for this, nodes are categorized into the components they belong in.
-Instead of initializing node scores to be a constant value such as 1, they are instead initialized to a score linear to the size of the component containing the nodes.
-Intuitively, this means that papers in larger components will receive higher scores, as desired.
+Instead of initializing node scores to be a constant value such as 1, they are
+instead initialized to a score linear to the size of the component containing
+the nodes. Intuitively, this means that papers in larger components will
+receive higher scores, as desired.
 
-A final variation on the basic scoring function is the incorporation of a damping factor $d$.
-A user following a citation chain will eventually stop, possibly at the end of the chain.
-Intuitively, the farther down a chain a user traverses, the less likely the papers will relevant and important to the original query, and the more likely the user will stop.
-The damping factor models this behaviour by reducing the change produced by the scoring function as the number of rounds increases.
-Adapted from PageRank, this results in the final version of our scoring function:\\
+A final variation on the basic scoring function is the incorporation of a
+damping factor $d$. A user following a citation chain will eventually stop,
+possibly at the end of the chain. Intuitively, the farther down a chain a user
+traverses, the less likely the papers will relevant and important to the
+original query, and the more likely the user will stop. The damping factor
+models this behavior by reducing the change produced by the scoring function
+as the number of rounds increases. Adapted from PageRank, this results in the
+final version of our scoring function:\\
 \begin{equation}
@@
 \end{equation}
-where $d$ is the damping factor, $N$ is the total number of papers/nodes in the network, and all other variables remain as defined.
+where $d$ is the damping factor, $N$ is the total number of papers/nodes in the
+network, and all other variables remain as defined.
 
@@
 
-For PubCrawl's implementation of the adapted PageRank scoring function, we used several parameters for variables defined in Section \ref{sec:pagerank}:\\
+For PubCrawl's implementation of the adapted PageRank scoring function, we used
+several parameters for variables defined in Section \ref{sec:pagerank}:\\
 
 \begin{itemize}
-\item For the score source $E$, we use a uniform value.
-We minimize the value of $E$ that still results in convergence, to reduce the total amount of freely created score.
-In our system, we found $E=0.1$ to be appropriate.
+\item For the score source $E$, we use a uniform value. We minimize the value
+  of $E$ that still results in convergence, to reduce the total amount of
+  freely created score. In our system, we found $E=0.1$ to be appropriate.
 
-\item For initializing node scores, we use a linear relationship with the size of the component containing the node.
-If the total number of papers (and nodes) is $N$ and paper $p$ is in a component with $X$ nodes, then the initial score for $p$ is set to $\frac{X}{N}$.
-Thus, larger components start with initially higher scores, and typically converge with higher final scores.
+\item For initializing node scores, we use a linear relationship with the size
+  of the component containing the node. If the total number of papers (and
+  nodes) is $N$ and paper $p$ is in a component with $X$ nodes, then the
+  initial score for $p$ is set to $\frac{X}{N}$. Thus, larger components start
+  with initially higher scores, and typically converge with higher final
+  scores.
 
-\item For the damping factor of our final scoring function (Equation \ref{eqn:damping}), we use $d=0.85$.
-This is a reflection of the PageRank study indicating this value as reasonable, rather than a precisely chosen one.
+\item For the damping factor of our final scoring function (Equation
+  \ref{eqn:damping}), we use $d=0.85$. This is a reflection of the PageRank
+  study indicating this value as reasonable, rather than a precisely chosen
+  one.
 

### 2012-05-15 report/paper.tex
More concisely describe what the system does

@@
 Digital Library. The system allows users to weight the relative importance of
-matches in the title, abstract, full text, and the PageRank of each hit,
-providing a platform to test further refinements of the algorithms. We evaluate
-the system in user studies.
+matches in various sections of the documents. We also implement a version of
+PageRank over the dataset. We evaluate the system in user studies.
 \end{abstract}

### 2012-05-15 index/Searcher.java
Don't bother working PageRank into Lucene's scoring
The result is the same as computing the combined score after the fact, just
more work

@@ -28,18 +28,16 @@ class Searcher {
       boosts.put("fulltext", Float.parseFloat(args[3]));
       QueryParser p = new MultiFieldQueryParser(Version.LUCENE_36, fields, a,
                                                 boosts);
-      ValueSourceQuery pagerank = new FieldScoreQuery("pagerank", FieldScoreQuery.Type.FLOAT);
       Scanner in = new Scanner(System.in);
       while (in.hasNextLine()) {
         Query q = p.parse(in.nextLine().trim());
-        TopDocs hits = s.search(q, 10);
+        TopDocs hits = s.search(q, 30);
         for (ScoreDoc d : hits.scoreDocs) {
           Document doc = s.doc(d.doc);
           float score = d.score;
           String title = doc.getFieldable("title").stringValue();
-          String pid = doc.getFieldable("proc_id").stringValue();
-          String aid = doc.getFieldable("article_id").stringValue();
-          System.out.format("%f %s (%s, %s)\n", score, title, pid, aid);
+          String pagerank = doc.getFieldable("pagerank").stringValue();
+          System.out.format("%d %f %s %s\n", d.doc, score, pagerank, title);
         }
       }
     }

### 2012-05-17 report/paper.tex
Implementation section and slides from poster session.

--- 2012-05-15 report/paper.tex
@@
 
-\title{PubCrawl: A Paper Search Engine}
+\title{PubCrawl: A Publication Search Engine}
 \author{Frank Li (frankli@mit.edu) \\
@@
 Additionally, Google Scholar has been shown to be heavily influenced by citation count, which may be inappropriate for some user queries.
+
+\section{ACM Data}
+%Information about ACM data
 
@@
 \label{sec:implementation}
+\subsection{Overview}
+PubCrawl is an online search website built with the Django web framework backed by a Postgres database and Lucene search index.
+While the Postgres database stores metadata about papers such as the citation graph, author and venue information, Lucene stores indexes for paper titles, abstracts and fulltext.
+The PubCrawl interface allows users to submit search terms and relative weights to be assigned to title, abstract, full text searches and pagerank.
+Figure \ref{interface} shows a screenshot of the interface.
 
-MANASI'S WEBSITE STUFF//
-%Manasi's website stuff
+\begin{figure}[t]
+\centering
+	\includegraphics[width=8in]{images/interface}
+	\caption{PubCrawl interface allowing search term and relative weight inputs.}	
+	\label{interface}
+\end{figure}
 
+\subsection{Scores and Scaling}
+PubCrawl combines four scores in all - a fulltext search score, a title search score, an abstract search score and the PageRank score.
+Since Lucene does't score on a pre-defined scale, we normalize all Lucene.
+Similarly, we normalize PageRanks.
+We normalize all scores on a per-query basis.
+This is particularly relevant to PageRank since results for a particular topic may all have low PageRank since the topic is studied by few researchers.
+By normalizing per-query, we do not penalize topics with a small number of papers.
+
+\subsection{Ranking}
+An important challenge faced by PubCrawl is how to effectively combine the four scores above to get an over quality score for a document.
+We implemented two types of simple ranking functions for this purpose:
+
+\begin{itemize}
+	\item 2-factor ranking: As a first step, we only allowed full text and page rank scores to be combined.
+We used a simple sorting technique for this since every document returned by the search has an associated full text and page rank score.
+	\item 4-factor ranking: In order to combine multiple scores, i.e., to combine multiple sorted lists, we used the RankJoin algorithm.
+Briefly, RankJoin is a top-k algorithm that takes multiple sorted lists and traverses them in a round-robin fashion performing hash joins on already seen tuples.
+It is able to stop before traversing all tuples because once the max possible score of unseen tuples becomes lesser than the minimum score of the top-k tuples, we are guaranteed to have the required top-k set of tuples.
+We implemented a slight variation of RankJoin since we don't need joins across all 4 lists.
+\end{itemize}
+
+\subsection{Tuning Parameters}
+
+To tune weights for the four factors, we obtained information about seminal papers on 6 topics from experts in the respective areas.
+We then manually picked weights that gave good results for all 6 topics.
+
+\subsection{PageRank Parameters}
 For PubCrawl's implementation of the adapted PageRank scoring function, we used several parameters for variables defined in Section \ref{sec:pagerank}:\\
@@
 
+To evaluate the quality of PubCrawl results, we performed a preliminary user study.
+In this study, we compared the quality of PubCrawl results with those from Google Scholar, Microsoft Academic Search, ACM Digital Library and CiteSeer.
+
+\subsection{Methodology}
+
+For 3 topics, we performed searches on Google Scholar, Microsoft Academic Search, ACM Digital Library, CiteSeer and PubCrawl.
+We then obtained lists of the top 10 ACM publication results from these search engines.
+We provided these lists to our experts.
+The experts rated each of the 10 results as Highly Relevant, Moderately Relevant and Not relevant.
+They also ranked the five lists in order of decreasing quality.
+Table \ref{} shows the results for the 3 test topics.
+
+We find that PubCrawl consistently does as well as CiteSeer and ACM DL.
+
+\subsection{Challenges}
+The main challenges with evaluating the user study were (1) Ground truth wasn't always clearly known, (2) Ground-truth is subjective, (3) since the data only included ACM papers, we had to discard a large number of highly relevant but non-ACM publications.
+
 \section{Results}
 
-\section{Conclusion}
+User study results.
+
+Some time comparisons.
+
+\section{Conclusion and Future Work}
+
+We observed that it is very difficult to find a scoring function that works well for all search queries.
+We also realized that combining scores from orthogonal metrics like PageRank and text indexing may not be the best method to obtain an overall ranking.
+
+Several extensions of this work are possible.
+An extremely challenging question we would like to answer is what is the best way to determine appropriate weights in a ranking function.
+Using labelled data points and curve fitting or SVMs, we are likely to get a better set of results.
+We would also like to investigate the following heuristics further: it would also be interesting to extend page rank so that it takes into account relationships between papers, i.e.
+paper A supports paper B, paper A refutes paper B etc.
+Similarly we would like to use metadata such as paper venues in order to further refine the scoring.
+We also looked into whether we could classify papers based on the level of expertise a paper expects.
+This may also be used to boost our search results.
 

### 2012-05-17 lucene/handout.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{fontspec}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{parskip}
\usepackage{sectsty}
\usepackage{unicode-math}

\defaultfontfeatures{Scale=MatchLowercase, Mapping=tex-text}
\setmainfont{Optima LT Std}
\setmathfont{Neo Euler}

\sectionfont{\fontspec[Scale=1.44]{Optima LT Std}}
\subsectionfont{\fontspec[Scale=1.2]{Optima LT Std}}

\begin{document}
\pagestyle{empty}
\Large

\section*{Indexing documents}

\begin{enumerate}
\item Parse XML: extract title, subtitle, abstract, full text, metadata
\item Tokenize, normalize, filter stopwords
\item Build inverted index
\end{enumerate}

\section*{Searching documents}

\subsection*{Filter documents using the Boolean Model}

\begin{enumerate}
\item Tokenize, normalize, filter the terms of the query
\item Rewrite the query in disjunctive normal form
\item Return documents which satisfy the query
\end{enumerate}

\subsection*{Score documents using the Vector Space Model}

Document and query are high-dimensional vectors

Cosine similarity:

\begin{equation*}
\mathrm{similarity}(q, d) = \frac{V(q) \cdot V(d)}{\vert V(q) \vert \vert V(d)
  \vert}
\end{equation*}

Adapted for Lucene:

\begin{equation*}
\mathrm{score}(q, d) = \mathrm{coord}(q,d) \mathrm{queryBoost}(q) \frac{V(q)
  \cdot V(d)}{\vert V(q) \vert} \mathrm{docNorm}(d) \mathrm{docBoost}(d)
\end{equation*}

Precompute some things and further generalize:

\begin{equation*}
  \mathrm{score}(q,d) = \mathrm{coord}(q,d)\mathrm{queryNorm}(q) \sum_{t \in q}
  \left( \mathrm{tf}(t, d) \mathrm{idf}(t)^2 \mathrm{boost}(t) \mathrm{norm}(t,
  d) \right)
\end{equation*}

\end{document}

### 2012-05-17 report/paper.tex

@@
 
+\begin{abstract}
+Searching for documents ranked by relevance is a well-studied problem for web
+pages. In particular, there are frameworks for estimating relevance as a
+function of the content of the document and algorithms for estimating relevance
+as a function of incoming links. However, further specialization of these
+techniques is required to search a corpus of academic papers. Academic papers
+are highly structured, lending additional weight to matches which appear in
+important sections such as the title or abstract. Moreover, citations have
+contextual information which changes the weight which should be contributed to
+cited papers. Here we describe PubCrawl, a search engine built for the ACM
+Digital Library. The system allows users to weight the relative importance of
+matches in various sections of the documents. We also implement a version of
+PageRank over the dataset. We evaluate the system in user studies.
+\end{abstract}
+
 \section{Introduction}
 
-	A primary source of information for computer science researchers are published papers from conference proceedings and journals.
-However, there are simply too many papers in published in too many venues to keep track of.
-While experienced researchers are typically versed in the famous and influential papers of their respective fields, they may be less familiar with other areas that might still be needed for their work.
-Less experienced researchers and students may have even less or no knowledge of the relevant papers of a subject.
+A primary source of information for computer science researchers are published
+papers from conference proceedings and journals. However, there are simply too
+many papers in published in too many venues to keep track of. While experienced
+researchers are typically versed in the famous and influential papers of their
+respective fields, they may be less familiar with other areas that might still
+be needed for their work. Less experienced researchers and students may have
+even less or no knowledge of the relevant papers of a subject.
 
-	To address this issue, researchers have create paper search engines, such as Google Scholar and CiteseerX.
-However, the ranking process for these systems is largely privately maintained.
-In this paper, we investigate the process of ranking in the academic papers setting.
-An understanding of this is important to create a better search system.
+To address this issue, researchers have create paper search engines, such as
+Google Scholar and CiteseerX. However, the ranking process for these systems is
+largely privately maintained. In this paper, we investigate the process of
+ranking in the academic papers setting. An understanding of this is important
+to create a better search system.
 
-	To do this, we designed PubCrawl, a paper search engine, as a testing bed for ranking mechanisms.
-In building PubCrawl, we used Apache Lucene for text indexing to measure a paper’s relevance to a query, and an adaptation of PageRank on the papers citation graph for weighting a paper’s importance.
-Currently all papers in the Association of Computing Machinery (ACM) Digital Library database have been processed.
-A simple web user interface is provided, where users can input queries and weights for what attributes they feel is most important, to tune the result rankings to fit what they feel is most appropriate.
-The top papers are returned, with hyperlinks to the papers’ ACM homepage.
+To do this, we designed PubCrawl, a paper search engine, as a testing bed for
+ranking mechanisms. In building PubCrawl, we used Apache Lucene for text
+indexing to measure a paper’s relevance to a query, and an adaptation of
+PageRank on the papers citation graph for weighting a paper’s importance.
+Currently all papers in the Association of Computing Machinery (ACM) Digital
+Library database have been processed. A simple web user interface is provided,
+where users can input queries and weights for what attributes they feel is most
+important, to tune the result rankings to fit what they feel is most
+appropriate. The top papers are returned, with hyperlinks to the papers’ ACM
+homepage.
 
-	In this report, we detail the design of PubCrawl and investigate the effects of many of its features.
-We conduct a user study to compare the performance of our ranking system versus other current systems.
+In this report, we detail the design of PubCrawl and investigate the effects of
+many of its features. We conduct a user study to compare the performance of our
+ranking system versus other current systems.
 
@@
 \begin{itemize}
-\item For the score source $E$, we use a uniform value.
-We minimize the value of $E$ that still results in convergence, to reduce the total amount of freely created score.
-In our system, we found $E=0.1$ to be appropriate.
+\item For the score source $E$, we use a uniform value. We minimize the value
+  of $E$ that still results in convergence, to reduce the total amount of
+  freely created score. In our system, we found $E=0.1$ to be appropriate.
 
-\item For initializing node scores, we use a linear relationship with the size of the component containing the node.
-If the total number of papers (and nodes) is $N$ and paper $p$ is in a component with $X$ nodes, then the initial score for $p$ is set to $\frac{X}{N}$.
-Thus, larger components start with initially higher scores, and typically converge with higher final scores.
+\item For initializing node scores, we use a linear relationship with the size
+  of the component containing the node. If the total number of papers (and
+  nodes) is $N$ and paper $p$ is in a component with $X$ nodes, then the
+  initial score for $p$ is set to $\frac{X}{N}$. Thus, larger components start
+  with initially higher scores, and typically converge with higher final
+  scores.
 
-\item For the damping factor of our final scoring function (Equation \ref{eqn:damping}), we use $d=0.85$.
-This is a reflection of the PageRank study indicating this value as reasonable, rather than a precisely chosen one.
+\item For the damping factor of our final scoring function (Equation
+  \ref{eqn:damping}), we use $d=0.85$. This is a reflection of the PageRank
+  study indicating this value as reasonable, rather than a precisely chosen
+  one.
 

### 2012-05-17 report/paper.tex
few updates
Combine introduction and related work

@@
 \setcounter{secnumdepth}{2} 
-
 \title{PubCrawl: A Publication Search Engine}
@@
 A primary source of information for computer science researchers are published
-papers from conference proceedings and journals. However, there are simply too
-many papers in published in too many venues to keep track of. While experienced
-researchers are typically versed in the famous and influential papers of their
-respective fields, they may be less familiar with other areas that might still
-be needed for their work. Less experienced researchers and students may have
-even less or no knowledge of the relevant papers of a subject.
+papers from conference proceedings and journals. As the number of papers and
+venues increases, the ability to quickly find papers relevant to a given topic
+becomes more important. In particular, researchers want search engines which
+return important papers.
 
-To address this issue, researchers have create paper search engines, such as
-Google Scholar and CiteseerX. However, the ranking process for these systems is
-largely privately maintained. In this paper, we investigate the process of
-ranking in the academic papers setting. An understanding of this is important
-to create a better search system.
+There are several existing search engines for academic papers, most prominently
+Google Scholar, \citeseer, and Microsoft Academic Search. Google Scholar uses a
+proprietary algorithm which combines several approaches. However, researchers
+have partially reverse engineered it \cite{beel09a, beel09b}. In particular,
+the algorithm is biased towards highly cited papers, which should highly rank
+important papers in the standard literature. However, the bias
+will also make the algorithm miss more recent influential papers. Researchers
+also uncovered several weaknesses in Google's automatic processing of documents
+which could allow authors to game search rankings \cite{beel10}.
 
-To do this, we designed PubCrawl, a paper search engine, as a testing bed for
-ranking mechanisms. In building PubCrawl, we used Apache Lucene for text
-indexing to measure a paper’s relevance to a query, and an adaptation of
-PageRank on the papers citation graph for weighting a paper’s importance.
-Currently all papers in the Association of Computing Machinery (ACM) Digital
-Library database have been processed. A simple web user interface is provided,
-where users can input queries and weights for what attributes they feel is most
-important, to tune the result rankings to fit what they feel is most
-appropriate. The top papers are returned, with hyperlinks to the papers’ ACM
-homepage.
+\citeseer\ is primarily an automatic citation indexing system \cite{giles98,
+  lawrence99, li06}. The system crawls the web and processes documents which
+appear to be academic papers. This approach produces a large corpus of noisy
+data, which hurts the performance of its ranking algorithm. Also,
+\citeseer\ does not make use of the citation data it processes in its ranking
+algorithm.
 
-In this report, we detail the design of PubCrawl and investigate the effects of
-many of its features. We conduct a user study to compare the performance of our
-ranking system versus other current systems.
+Microsoft Academic Search is a relatively new search engine designed to compete
+with Google Scholar. It too uses a proprietary algorithm which combines several
+features, and shows the same weakness to ranking optimization as Scholar.
 
-\section{Related Work}
-
-There are a few paper search engines currently in existence, such as CiteseerX
-and Google Scholar. Their ranking process is largely maintained privately, but
-several characteristics of both are described in this section.
-
-CiteseerX's data set is scraped from the web by a crawler, and processed in an
-automated fashion. This has provided CiteseerX with wide and largely hands-off
-coverage of papers. However, due to the purely automated approach used and the
-heterogeneity in data representation on the web, the data collected contains
-errors and missing information. For example, the crawler has mistaken the wrong
-string for the title of a number of papers. This leads to some errors in the
-processing of both the paper data and queries.
-
-Google Scholar also operates with a crawler, and exhibits some of the same
-dirty data issues as CiteseerX. Additionally, Google Scholar has been shown to
-be heavily influenced by citation count, which may be inappropriate for some
-user queries.
+Here, we present PubCrawl, a system built to test ranking algorithms for
+searching academic papers. The system searches over the complete ACM Digital
+Library. We use Apache Lucene to index documents and estimate relevance and
+PageRank to estimate importance. The system provides a web interface using the
+Django web framework backed by a Postgres database. Users can input queries and
+relative weights for matches in various sections of the document as well as the
+PageRank.
 
@@
 \section{Acknowledgments}
-\null
+
+\bibliography{refs}{}
+\bibliographystyle{acm}
 
 \end{document}
+
+\end{document}

### 2012-05-17 report/paper.tex
Initial writeup of Lucene stuff
Omit actual equations for brevity, since we basically used the scoring as a
black box.

@@
 
-\subsection{Lucene Text Indexing}
-%Abhishek
+\subsection{Document scores}
+
+We use Apache Lucene \cite{lucene} to index documents and provide scores based
+on the content of documents. We build the usual inverted index over the corpus,
+filtering out stopwords. The structure of the documents is preserved in the XML
+corpus, so we can index titles, subtitles, abstracts, and full text as separate
+fields. We also include various metadata to simplify the implementation of the
+front-end.
+
+Lucene uses the Boolean model \cite{lancaster73} to filter documents and the
+Vector Space Model \cite{salton75} to score documents. Documents $d$ and
+queries $q$ are vectors $V(\cdot)$ with each term a dimension and coordinates
+equal to tf*idf values. Then, the relevance of a document to a query is related
+to the angle between them (the cosine similarity score). Lucene generalizes the
+cosine similarity score in several ways. First, documents are allowed to have
+multiple and duplicate fields. Second, Lucene allows index-time boosting of
+documents and fields as well as query-time boosting of query terms. Finally,
+Lucene does not require every term to appear in hits, instead using a
+coordination factor to score documents which contain more terms higher. These
+features can be exploited to improve the quality of search results.
 

### 2012-05-17 report/paper.tex
Fix preamble
Set margins, and include a macro for rendering "SiteSeerX"
Remove unnecessary notation

@@
 \usepackage{graphicx}
+\usepackage[letterpaper,margin=1in]{geometry}
+
+\newcommand{\citeseer}{CiteSeer$^\chi$}
 
@@
 \begin{abstract}
-Searching for documents ranked by relevance is a well-studied problem for web
-pages. In particular, there are frameworks for estimating relevance as a
-function of the content of the document and algorithms for estimating relevance
-as a function of incoming links. However, further specialization of these
-techniques is required to search a corpus of academic papers. Academic papers
-are highly structured, lending additional weight to matches which appear in
-important sections such as the title or abstract. Moreover, citations have
-contextual information which changes the weight which should be contributed to
-cited papers. Here we describe PubCrawl, a search engine built for the ACM
-Digital Library. The system allows users to weight the relative importance of
-matches in various sections of the documents. We also implement a version of
-PageRank over the dataset. We evaluate the system in user studies.
+Searching for documents ranked by relevance is a well-studied problem in
+information retrieval. In particular, there are frameworks for estimating
+relevance as a function of the content of the document and algorithms for
+estimating relevance as a function of incoming links. However, further
+specialization of these techniques is required to search a corpus of academic
+papers. Academic papers are highly structured, lending additional weight to
+matches which appear in important sections such as the title or abstract.
+Contextual information changes the weight which should be contributed to cited
+papers. Here we describe PubCrawl, a search engine built for the ACM Digital
+Library. The system allows users to weight the relative importance of matches
+in various sections of the documents. We also implement a version of PageRank
+over the dataset. We evaluate the system in user studies.
 \end{abstract}
@@
 Lucene uses the Boolean model \cite{lancaster73} to filter documents and the
-Vector Space Model \cite{salton75} to score documents. Documents $d$ and
-queries $q$ are vectors $V(\cdot)$ with each term a dimension and coordinates
-equal to tf*idf values. Then, the relevance of a document to a query is related
-to the angle between them (the cosine similarity score). Lucene generalizes the
-cosine similarity score in several ways. First, documents are allowed to have
-multiple and duplicate fields. Second, Lucene allows index-time boosting of
-documents and fields as well as query-time boosting of query terms. Finally,
-Lucene does not require every term to appear in hits, instead using a
-coordination factor to score documents which contain more terms higher. These
-features can be exploited to improve the quality of search results.
+Vector Space Model \cite{salton75} to score documents. Documents and queries
+are vectors with each term a dimension and coordinates equal to tf*idf values.
+Then, the relevance of a document to a query is related to the angle between
+them (the cosine similarity score). Lucene generalizes the cosine similarity
+score in several ways. First, documents are allowed to have multiple and
+duplicate fields. Second, Lucene allows index-time boosting of documents and
+fields as well as query-time boosting of query terms. Finally, Lucene does not
+require every term to appear in hits, instead using a coordination factor to
+score documents which contain more terms higher. These features can be
+exploited to improve the quality of search results.
 

### 2012-05-17 report/paper.tex
Initial writeup about ACM data
Move statistics about the citation graph here

@@
 
-\section{ACM Data}
-%Information about ACM data
-
 \section{PubCrawl Design}
 
-PubCrawl is designed to rank papers based on relevance and importance. To
-measure relevance, we use Apache Lucene, a high-performance text search engine
-library for Java. Lucene is used to provide text indexing, returning the papers
-most textually relevant to a query. To measure importance, we use a variation
-of the classic PageRank algorithm on the citation graph of papers. The
-weighting between the text indexing and PageRank score is an input the users
-can provide, as discussed in \ref{sec:implementation}. Currently, the ACM
-dataset has been gathered and applied using PubCrawl. Through the design of the
-system, we discuss the effect of a number of its features.
+\section{ACM Digital Library}
+
+The ACM Digital Library is a corpus of over 223,800 academic papers published
+in ACM journals or conference proceedings. The data set is in XML format with
+rich metadata including citations. Unlike \citeseer, we do not have to do
+sophisticated NLP to build a citation graph, increasing the quality of the
+resulting graph.
+
+However, because the data set is limited to ACM publications, the citation
+graph is highly disconnected. Although the vast majority of the papers
+(176,285) are contained in one component, in total there are 45,571 connected
+components. Figure \ref{comp-size} shows the size distribution of these
+components is heavily skewed. We take special consideration of component size
+in our adaptation of the PageRank algorithm.
+
+\begin{figure}[ht]
+  \begin{center}
+    \includegraphics[width=5in]{images/component-graph}
+  \end{center}
+  \caption{Distribution of component sizes in the citation graph}
+  \label{comp-size}
+\end{figure}
 
@@
 While the Postgres database stores metadata about papers such as the citation graph, author and venue information, Lucene stores indexes for paper titles, abstracts and fulltext.
-The PubCrawl interface allows users to submit search terms and relative weights to be assigned to title, abstract, full text searches and pagerank.
+The PubCrawl interface allows users to submit search terms and relative weights to be assigned to title, abstract, full text searches and PageRank.
 Figure \ref{interface} shows a screenshot of the interface.
@@
 To evaluate the quality of PubCrawl results, we performed a preliminary user study.
-In this study, we compared the quality of PubCrawl results with those from Google Scholar, Microsoft Academic Search, ACM Digital Library and CiteSeer.
+In this study, we compared the quality of PubCrawl results with those from Google Scholar, Microsoft Academic Search, ACM Digital Library and \citeseer.
 
@@
 An extremely challenging question we would like to answer is what is the best way to determine appropriate weights in a ranking function.
-Using labelled data points and curve fitting or SVMs, we are likely to get a better set of results.
+Using labeled data points and curve fitting or SVMs, we are likely to get a better set of results.
 We would also like to investigate the following heuristics further: it would also be interesting to extend page rank so that it takes into account relationships between papers, i.e.

### 2012-05-17 report/paper.tex
Simplify description of PageRank
Don't re-derive the algorithm, just cite the paper and state what we changed

@@
 
-The relationship between academic papers draws a strong analogy with that
-between web pages. Just as pages on the web embed links to other pages, papers
-cite other papers. This forms a directed graph of paper nodes and citation
-edges, where an edge from one paper $A$ to another paper $B$ indicates that $A$
-cited $B$.
-
-To exploit the similarity between the two environments, we use a variation of
-the PageRank algorithm. PageRank is an algorithm used by the Google search
-engine that provides a weighted score for web pages based on the number of
-external pages that cite a particular web page, and the PageRank of those
-external pages. We use a similar framework for academic papers, where a paper's
-score is based on the number of other papers citing it, and the score of those
-papers. The most simple form of this captured by the following equation:\\
-\begin{equation}
-\label{eqn:basic}
-S(p)= \Sigma_{c \in C} \frac{S(c)}{D(c)}
-\end{equation}
-where $p$ is the paper being scored, $C$ is the set of all papers that cite
-$p$, $S$ is the scoring function, and $D$ is the degree function (indicating
-the number of papers a certain paper cites).
-
-The score of all nodes can be calculated in an iterative manner. All nodes can
-be initialized to a default score, such as 1. Then, in each round, Equation
-\ref{eqn:basic} can be applied to all nodes. This process is repeated until
-node scores converge. However, this scoring function is further complicated by
-a couple of features of academic paper relations: cycles and components.
-
-Citation cycles provide one source of complication. In citation cycles, a
-paper's chain of citations returns to the paper itself. A number of these
-cycles exist in the data set. In general, these cycles act as a score sink,
-shifting the score of external nodes into the cycle round after round. Inside
-the cycle, the score rotates among nodes, preventing convergence. To reduce the
-impact of these cycles, a score source is provided for node each round, as also
-done in PageRank. To provide convergence, the total sum of all node scores must
-remain constant, so node scores must be normalized per round. This results in
-an updated scoring function of:\\
-\begin{equation}
-\label{eqn:cycle}
-S(p)= n(\Sigma_{c \in C} \frac{S(c)}{D(c)}+E(p))
-\end{equation}
-where $E$ is a source of score, $n$ is the normalization factor, and all other
-variables remain as defined.
-
-\begin{figure}[t]
-\centering \includegraphics[width=5in]{images/component-graph}
-	\caption{Sizes of components in the ACM data set and the number of each
-      size's occurrence.}
-	\label{comp-size}
-\end{figure}
-
-Components in the citation graph are the other source of complication. Papers
-in the same component are either both part of the same citation chain or share
-a common ancestor or descendant in their respective chain. The ACM data
-exhibits 45,571 total components, with one large component of 176,285 papers,
-and a large number of smaller components ranging in size from one to ten
-papers, as displayed in Figure \ref{comp-size}. Small components are papers
-that don't cite many or any other papers in the data set and aren't heavily
-cited. This implies that nodes in small components should not be highly ranked.
-
-To adjust for this, nodes are categorized into the components they belong in.
-Instead of initializing node scores to be a constant value such as 1, they are
-instead initialized to a score linear to the size of the component containing
-the nodes. Intuitively, this means that papers in larger components will
-receive higher scores, as desired.
-
-A final variation on the basic scoring function is the incorporation of a
-damping factor $d$. A user following a citation chain will eventually stop,
-possibly at the end of the chain. Intuitively, the farther down a chain a user
-traverses, the less likely the papers will relevant and important to the
-original query, and the more likely the user will stop. The damping factor
-models this behavior by reducing the change produced by the scoring function
-as the number of rounds increases. Adapted from PageRank, this results in the
-final version of our scoring function:\\
-\begin{equation}
-\label{eqn:damping}
-S(p)= n(\frac{1-d}{N}+d(\Sigma_{c \in C} \frac{S(c)}{D(c)}+E(p)))
-\end{equation}
-where $d$ is the damping factor, $N$ is the total number of papers/nodes in the
-network, and all other variables remain as defined.
+PageRank is a well-known algorithm for estimating the importance of a web page
+as a function of the number of incoming links \cite{brin98, page99}. It is
+plausible to extend the algorithm by analogy to academic papers and citations.
+However, applying PageRank directly to the ACM citation graph gives suboptimal
+results due to the high number of small components. Papers in these components
+end with disproportionately high PageRank because further iterations do not
+change their initial value very much. Instead of a constant, we set the initial
+value of a paper's PageRank to the proportion of all papers contained in its
+component.
 

### 2012-05-17 report/paper.tex
Combine design and implementation sections
Move overview of the system to the top, move PageRank stuff to that section

--- 2012-05-17 report/paper.tex
@@
 
-\section{PubCrawl Design}
+\section{PubCrawl Design and Implementation}
 
-\section{ACM Digital Library}
+\subsection{Overview}
+
+PubCrawl is an online search website for the ACM Digital Library built with the
+Django web framework. It is backed by a Postgres database which stores metadata
+(authors, venues, and citations) and a Lucene search index. The PubCrawl
+interface allows users to submit search terms and assign relative weights to
+title, abstract, and full text searches and PageRank. Figure \ref{interface}
+shows a screenshot of the interface.
+
+\begin{figure}[bt]
+  \begin{center}
+    \includegraphics[width=8in]{images/interface}
+  \end{center}
+  \caption{PubCrawl user interface}
+  \label{interface}
+\end{figure}
+
+\subsection{ACM Digital Library}
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[tb]
   \begin{center}
@@
 \subsection{Adapted PageRank}
-\label{sec:pagerank}
 
@@
 plausible to extend the algorithm by analogy to academic papers and citations.
-However, applying PageRank directly to the ACM citation graph gives suboptimal
-results due to the high number of small components. Papers in these components
-end with disproportionately high PageRank because further iterations do not
-change their initial value very much. Instead of a constant, we set the initial
-value of a paper's PageRank to the proportion of all papers contained in its
-component.
+We use the iterative algorithm as described but tune the parameters to improve
+the quality of the results for the ACM data set.
 
-\section{Implementation}
-\label{sec:implementation}
-\subsection{Overview}
-PubCrawl is an online search website built with the Django web framework backed by a Postgres database and Lucene search index.
-While the Postgres database stores metadata about papers such as the citation graph, author and venue information, Lucene stores indexes for paper titles, abstracts and fulltext.
-The PubCrawl interface allows users to submit search terms and relative weights to be assigned to title, abstract, full text searches and PageRank.
-Figure \ref{interface} shows a screenshot of the interface.
+We set the score source $E$ to a uniform vector with each coordinate equal to
+$0.1$. This setting minimizes the PageRank each paper gets for free while still
+allowing the algorithm to converge. We set the damping factor $d$ to the
+suggested value of $0.85$. This setting reduces the number of iterations needed
+to converge by reducing the amount of PageRank contributed in subsequent
+iterations.
 
-\begin{figure}[t]
-\centering
-	\includegraphics[width=8in]{images/interface}
-	\caption{PubCrawl interface allowing search term and relative weight inputs.}	
-	\label{interface}
-\end{figure}
+We found initializing the PageRank of each paper to a constant gave suboptimal
+results because the ACM citation graph has a high number of small components.
+Papers in these components end with disproportionately high PageRank because
+further iterations do not change their initial value very much. Instead, we set
+the initial value of a paper's PageRank to the proportion of all papers
+contained in its component.
 
-\subsection{Scores and Scaling}
-PubCrawl combines four scores in all - a fulltext search score, a title search score, an abstract search score and the PageRank score.
-Since Lucene does't score on a pre-defined scale, we normalize all Lucene.
-Similarly, we normalize PageRanks.
-We normalize all scores on a per-query basis.
-This is particularly relevant to PageRank since results for a particular topic may all have low PageRank since the topic is studied by few researchers.
-By normalizing per-query, we do not penalize topics with a small number of papers.
+\subsection{Combining document scores and PageRanks}
 
-\subsection{Ranking}
-An important challenge faced by PubCrawl is how to effectively combine the four scores above to get an over quality score for a document.
-We implemented two types of simple ranking functions for this purpose:
+We compute a final score used for ranking documents as a linear function of
+subscores. One issue is that these subscores are not necessarily on the same
+scale. In particular, Lucene scores are on an arbitrary scale. To address this
+issue, we normalize scores per query.
 
-\begin{itemize}
-	\item 2-factor ranking: As a first step, we only allowed full text and page rank scores to be combined.
-We used a simple sorting technique for this since every document returned by the search has an associated full text and page rank score.
-	\item 4-factor ranking: In order to combine multiple scores, i.e., to combine multiple sorted lists, we used the RankJoin algorithm.
-Briefly, RankJoin is a top-k algorithm that takes multiple sorted lists and traverses them in a round-robin fashion performing hash joins on already seen tuples.
-It is able to stop before traversing all tuples because once the max possible score of unseen tuples becomes lesser than the minimum score of the top-k tuples, we are guaranteed to have the required top-k set of tuples.
-We implemented a slight variation of RankJoin since we don't need joins across all 4 lists.
-\end{itemize}
+The PageRank algorithm includes a normalization step at each iteration.
+However, if a particular topic is studied by only a few researchers, all the
+papers relevant to that topic will have low PageRank. To address this issue, we
+renormalize PageRanks per query.
 
-\subsection{Tuning Parameters}
+We implemented two ranking functions. The first only uses the full text score
+and PageRank. The second uses a rank join--inspired algorithm to combine lists
+of hits sorted by each of title, abstract, and full text scores and PageRank.
+Briefly, the algorithm maintains the top $k$ hits seen so far. In each
+iteration, we pop the maximum element off of the next list in round-robin order
+and hash it. When we encounter a duplicate, we update the combined score and
+its position in the top $k$. The algorithm terminates when the maximum possible
+score of unseen tuples is less than the score of the $k$th hit.
 
-To tune weights for the four factors, we obtained information about seminal papers on 6 topics from experts in the respective areas.
-We then manually picked weights that gave good results for all 6 topics.
-
-\subsection{PageRank Parameters}
-For PubCrawl's implementation of the adapted PageRank scoring function, we used several parameters for variables defined in Section \ref{sec:pagerank}:\\
-
-\begin{itemize}
-\item For the score source $E$, we use a uniform value. We minimize the value
-  of $E$ that still results in convergence, to reduce the total amount of
-  freely created score. In our system, we found $E=0.1$ to be appropriate.
-
-\item For initializing node scores, we use a linear relationship with the size
-  of the component containing the node. If the total number of papers (and
-  nodes) is $N$ and paper $p$ is in a component with $X$ nodes, then the
-  initial score for $p$ is set to $\frac{X}{N}$. Thus, larger components start
-  with initially higher scores, and typically converge with higher final
-  scores.
-
-\item For the damping factor of our final scoring function (Equation
-  \ref{eqn:damping}), we use $d=0.85$. This is a reflection of the PageRank
-  study indicating this value as reasonable, rather than a precisely chosen
-  one.
-
-\end{itemize}
+To tune weights for the four factors, we obtained information about important
+papers on 6 topics from experts in the respective areas. We then manually
+picked weights that gave good results for all 6 topics.
 

### 2012-05-17 report/paper.tex
Expand important details about Lucene
Talk about what Lucene scoring is doing under the covers and how it affects
what we're trying to do

@@
 
-We use Apache Lucene \cite{lucene} to index documents and provide scores based
-on the content of documents. We build the usual inverted index over the corpus,
-filtering out stopwords. The structure of the documents is preserved in the XML
-corpus, so we can index titles, subtitles, abstracts, and full text as separate
-fields. We also include various metadata to simplify the implementation of the
+We use Apache Lucene \cite{lucene} to index documents and compute relevance
+scores. We build the usual inverted index over the corpus, filtering out
+stopwords. The structure of the documents is preserved in the XML corpus, so we
+can easily parse titles, subtitles, abstracts, and full text. Lucene supports
+multi-field documents, so we index and perform searches on each independently.
+We also include various metadata to simplify the implementation of the
 front-end.
@@
 require every term to appear in hits, instead using a coordination factor to
-score documents which contain more terms higher. These features can be
-exploited to improve the quality of search results.
+score documents which contain more terms higher.
+
+While these features can be exploited to improve the quality of search results,
+they also have some unintended side effects. In particular, Lucene's scoring is
+biased towards matches in shorter fields due to the way it normalizes even
+though fields are boosted equally by default. We investigated using user
+inputted weights to boost individual fields within Lucene's scoring mechanism,
+but found it as difficult to combine the resulting scores with PageRank as
+performing three separate searches and combining four scores.
 

### 2012-05-17 report/paper.tex
Include the PageRank equation to explain the parameters we set

@@
 We use the iterative algorithm as described but tune the parameters to improve
-the quality of the results for the ACM data set.
+the quality of the results for the ACM data set. The update rule is:
 
-We set the score source $E$ to a uniform vector with each coordinate equal to
-$0.1$. This setting minimizes the PageRank each paper gets for free while still
-allowing the algorithm to converge. We set the damping factor $d$ to the
-suggested value of $0.85$. This setting reduces the number of iterations needed
-to converge by reducing the amount of PageRank contributed in subsequent
-iterations.
+\begin{equation}
+R(p)= n\left(\frac{1 - d}{N} + d\left(\sum_{c \in C}
+\frac{R(c)}{D(c)}+E(p)\right)\right)
+\end{equation}
+
+where $R(\cdot)$ is the PageRank of a node, $D(\cdot)$ is the outdegree of a
+node, $E(\cdot)$ is the score source of a node (needed to converge with
+cycles), $d$ is the damping factor, and $n$ is the normalizing factor.
+
+We set $E$ to a uniform vector with each coordinate equal to $0.1$. This
+setting minimizes the PageRank each paper gets for free while still allowing
+the algorithm to converge. We set $d$ to the suggested value of $0.85$. This
+setting reduces the number of iterations needed to converge by reducing the
+amount of PageRank contributed in subsequent iterations.
 

### 2012-05-18 report/paper.tex
User-study details.

--- 2012-05-17 report/paper.tex
@@
 \setcounter{secnumdepth}{2}
+
 \title{PubCrawl: A Publication Search Engine}
@@
 \usepackage{graphicx}
-\usepackage[letterpaper,margin=1in]{geometry}
-
-\newcommand{\citeseer}{CiteSeer$^\chi$}
 
@@
 
-\begin{abstract}
-Searching for documents ranked by relevance is a well-studied problem in
-information retrieval. In particular, there are frameworks for estimating
-relevance as a function of the content of the document and algorithms for
-estimating relevance as a function of incoming links. However, further
-specialization of these techniques is required to search a corpus of academic
-papers. Academic papers are highly structured, lending additional weight to
-matches which appear in important sections such as the title or abstract.
-Contextual information changes the weight which should be contributed to cited
-papers. Here we describe PubCrawl, a search engine built for the ACM Digital
-Library. The system allows users to weight the relative importance of matches
-in various sections of the documents. We also implement a version of PageRank
-over the dataset. We evaluate the system in user studies.
-\end{abstract}
-
 \section{Introduction}
 
-A primary source of information for computer science researchers are published
-papers from conference proceedings and journals. As the number of papers and
-venues increases, the ability to quickly find papers relevant to a given topic
-becomes more important. In particular, researchers want search engines which
-return important papers.
+	A primary source of information for computer science researchers are published papers from conference proceedings and journals.
+However, there are simply too many papers in published in too many venues to keep track of.
+While experienced researchers are typically versed in the famous and influential papers of their respective fields, they may be less familiar with other areas that might still be needed for their work.
+Less experienced researchers and students may have even less or no knowledge of the relevant papers of a subject.
 
-There are several existing search engines for academic papers, most prominently
-Google Scholar, \citeseer, and Microsoft Academic Search. Google Scholar uses a
-proprietary algorithm which combines several approaches. However, researchers
-have partially reverse engineered it \cite{beel09a, beel09b}. In particular,
-the algorithm is biased towards highly cited papers, which should highly rank
-important papers in the standard literature. However, the bias
-will also make the algorithm miss more recent influential papers. Researchers
-also uncovered several weaknesses in Google's automatic processing of documents
-which could allow authors to game search rankings \cite{beel10}.
+	To address this issue, researchers have create paper search engines, such as Google Scholar and CiteseerX.
+However, the ranking process for these systems is largely privately maintained.
+In this paper, we investigate the process of ranking in the academic papers setting.
+An understanding of this is important to create a better search system.
 
-\citeseer\ is primarily an automatic citation indexing system \cite{giles98,
-  lawrence99, li06}. The system crawls the web and processes documents which
-appear to be academic papers. This approach produces a large corpus of noisy
-data, which hurts the performance of its ranking algorithm. Also,
-\citeseer\ does not make use of the citation data it processes in its ranking
-algorithm.
+	To do this, we designed PubCrawl, a paper search engine, as a testing bed for ranking mechanisms.
+In building PubCrawl, we used Apache Lucene for text indexing to measure a paper’s relevance to a query, and an adaptation of PageRank on the papers citation graph for weighting a paper’s importance.
+Currently all papers in the Association of Computing Machinery (ACM) Digital Library database have been processed.
+A simple web user interface is provided, where users can input queries and weights for what attributes they feel is most important, to tune the result rankings to fit what they feel is most appropriate.
+The top papers are returned, with hyperlinks to the papers’ ACM homepage.
 
-Microsoft Academic Search is a relatively new search engine designed to compete
-with Google Scholar. It too uses a proprietary algorithm which combines several
-features, and shows the same weakness to ranking optimization as Scholar.
+	In this report, we detail the design of PubCrawl and investigate the effects of many of its features.
+We conduct a user study to compare the performance of our ranking system versus other current systems.
 
-Here, we present PubCrawl, a system built to test ranking algorithms for
-searching academic papers. The system searches over the complete ACM Digital
-Library. We use Apache Lucene to index documents and estimate relevance and
-PageRank to estimate importance. The system provides a web interface using the
-Django web framework backed by a Postgres database. Users can input queries and
-relative weights for matches in various sections of the document as well as the
-PageRank.
+\section{Related Work}
 
-\section{PubCrawl Design and Implementation}
+There are a few paper search engines currently in existence, such as CiteseerX and Google Scholar.
+Their ranking process is largely maintained privately, but several characteristics of both are described in this section.
 
+CiteseerX's data set is scraped from the web by a crawler, and processed in an automated fashion.
+This has provided CiteseerX with wide and largely hands-off coverage of papers.
+However, due to the purely automated approach used and the heterogeneity in data representation on the web, the data collected contains errors and missing information.
+For example, the crawler has mistaken the wrong string for the title of a number of papers.
+This leads to some errors in the processing of both the paper data and queries.
+
+Google Scholar also operates with a crawler, and exhibits some of the same dirty data issues as CiteseerX.
+Additionally, Google Scholar has been shown to be heavily influenced by citation count, which may be inappropriate for some user queries.
+
+\section{ACM Data}
+%Information about ACM data
+
+\section{PubCrawl Design}
+
+PubCrawl is designed to rank papers based on relevance and importance.
+To measure relevance, we use Apache Lucene, a high-performance text search engine library for Java.
+Lucene is used to provide text indexing, returning the papers most textually relevant to a query.
+To measure importance, we use a variation of the classic PageRank algorithm on the citation graph of papers.
+The weighting between the text indexing and PageRank score is an input the users can provide, as discussed in \ref{sec:implementation}.
+Currently, the ACM dataset has been gathered and applied using PubCrawl.
+Through the design of the system, we discuss the effect of a number of its features.
+
+\subsection{Lucene Text Indexing}
+%Abhishek
+
+\subsection{Adapted PageRank}
+\label{sec:pagerank}
+
+The relationship between academic papers draws a strong analogy with that between web pages.
+Just as pages on the web embed links to other pages, papers cite other papers.
+This forms a directed graph of paper nodes and citation edges, where an edge from one paper $A$ to another paper $B$ indicates that $A$ cited $B$.
+
+To exploit the similarity between the two environments, we use a variation of the PageRank algorithm.
+PageRank is an algorithm used by the Google search engine that provides a weighted score for web pages based on the number of external pages that cite a particular web page, and the PageRank of those external pages.
+We use a similar framework for academic papers, where a paper's score is based on the number of other papers citing it, and the score of those papers.
+The most simple form of this captured by the following equation:\\
+\begin{equation}
+\label{eqn:basic}
+S(p)= \Sigma_{c \in C} \frac{S(c)}{D(c)}
+\end{equation}
+where $p$ is the paper being scored, $C$ is the set of all papers that cite $p$, $S$ is the scoring function, and $D$ is the degree function (indicating the number of papers a certain paper cites).
+
+The score of all nodes can be calculated in an iterative manner.
+All nodes can be initialized to a default score, such as 1.
+Then, in each round, Equation \ref{eqn:basic} can be applied to all nodes.
+This process is repeated until node scores converge.
+However, this scoring function is further complicated by a couple of features of academic paper relations: cycles and components.
+
+Citation cycles provide one source of complication.
+In citation cycles, a paper's chain of citations returns to the paper itself.
+A number of these cycles exist in the data set.
+In general, these cycles act as a score sink, shifting the score of external nodes into the cycle round after round.
+Inside the cycle, the score rotates among nodes, preventing convergence.
+To reduce the impact of these cycles, a score source is provided for node each round, as also done in PageRank.
+To provide convergence, the total sum of all node scores must remain constant, so node scores must be normalized per round.
+This results in an updated scoring function of:\\
+\begin{equation}
+\label{eqn:cycle}
+S(p)= n(\Sigma_{c \in C} \frac{S(c)}{D(c)}+E(p))
+\end{equation}
+where $E$ is a source of score, $n$ is the normalization factor, and all other variables remain as defined.
+
+\begin{figure}[t]
+\centering
+	\includegraphics[width=5in]{images/component-graph}
+	\caption{Sizes of components in the ACM data set and the number of each size's occurrence.}	
+	\label{comp-size}
+\end{figure}
+
+Components in the citation graph are the other source of complication.
+Papers in the same component are either both part of the same citation chain or share a common ancestor or descendant in their respective chain.
+The ACM data exhibits 45,571 total components, with one large component of 176,285 papers, and a large number of smaller components ranging in size from one to ten papers, as displayed in Figure \ref{comp-size}.
+Small components are papers that don't cite many or any other papers in the data set and aren't heavily cited.
+This implies that nodes in small components should not be highly ranked.
+
+To adjust for this, nodes are categorized into the components they belong in.
+Instead of initializing node scores to be a constant value such as 1, they are instead initialized to a score linear to the size of the component containing the nodes.
+Intuitively, this means that papers in larger components will receive higher scores, as desired.
+
+A final variation on the basic scoring function is the incorporation of a damping factor $d$.
+A user following a citation chain will eventually stop, possibly at the end of the chain.
+Intuitively, the farther down a chain a user traverses, the less likely the papers will relevant and important to the original query, and the more likely the user will stop.
+The damping factor models this behaviour by reducing the change produced by the scoring function as the number of rounds increases.
+Adapted from PageRank, this results in the final version of our scoring function:\\
+\begin{equation}
+\label{eqn:damping}
+S(p)= n(\frac{1-d}{N}+d(\Sigma_{c \in C} \frac{S(c)}{D(c)}+E(p)))
+\end{equation}
+where $d$ is the damping factor, $N$ is the total number of papers/nodes in the network, and all other variables remain as defined.
+
+\section{Implementation}
+\label{sec:implementation}
 \subsection{Overview}
+PubCrawl is an online search website built with the Django web framework backed by a Postgres database and Lucene search index.
+While the Postgres database stores metadata about papers such as the citation graph, author and venue information, Lucene stores indexes for paper titles, abstracts and fulltext.
+The PubCrawl interface allows users to submit search terms and relative weights to be assigned to title, abstract, full text searches and pagerank.
+Figure \ref{interface} shows a screenshot of the interface.
 
-PubCrawl is an online search website for the ACM Digital Library built with the
-Django web framework. It is backed by a Postgres database which stores metadata
-(authors, venues, and citations) and a Lucene search index. The PubCrawl
-interface allows users to submit search terms and assign relative weights to
-title, abstract, and full text searches and PageRank. Figure \ref{interface}
-shows a screenshot of the interface.
-
-\begin{figure}[bt]
-  \begin{center}
+\begin{figure}[t]
+\centering
 	\includegraphics[width=8in]{images/interface}
-  \end{center}
-  \caption{PubCrawl user interface}
+	\caption{PubCrawl interface allowing search term and relative weight inputs.}	
 	\label{interface}
@@
 
-\subsection{ACM Digital Library}
+\subsection{Scores and Scaling}
+PubCrawl combines four scores in all - a fulltext search score, a title search score, an abstract search score and the PageRank score.
+Since Lucene does't score on a pre-defined scale, we normalize all Lucene.
+Similarly, we normalize PageRanks.
+We normalize all scores on a per-query basis.
+This is particularly relevant to PageRank since results for a particular topic may all have low PageRank since the topic is studied by few researchers.
+By normalizing per-query, we do not penalize topics with a small number of papers.
 
-The ACM Digital Library is a corpus of over 223,800 academic papers published
-in ACM journals or conference proceedings. The data set is in XML format with
-rich metadata including citations. Unlike \citeseer, we do not have to do
-sophisticated NLP to build a citation graph, increasing the quality of the
-resulting graph.
+\subsection{Ranking}
+An important challenge faced by PubCrawl is how to effectively combine the four scores above to get an over quality score for a document.
+We implemented two types of simple ranking functions for this purpose:
 
-However, because the data set is limited to ACM publications, the citation
-graph is highly disconnected. Although the vast majority of the papers
-(176,285) are contained in one component, in total there are 45,571 connected
-components. Figure \ref{comp-size} shows the size distribution of these
-components is heavily skewed. We take special consideration of component size
-in our adaptation of the PageRank algorithm.
+\begin{itemize}
+	\item 2-factor ranking: As a first step, we only allowed full text and page rank scores to be combined.
+We used a simple sorting technique for this since every document returned by the search has an associated full text and page rank score.
+	\item 4-factor ranking: In order to combine multiple scores, i.e., to combine multiple sorted lists, we used the RankJoin algorithm.
+Briefly, RankJoin is a top-k algorithm that takes multiple sorted lists and traverses them in a round-robin fashion performing hash joins on already seen tuples.
+It is able to stop before traversing all tuples because once the max possible score of unseen tuples becomes lesser than the minimum score of the top-k tuples, we are guaranteed to have the required top-k set of tuples.
+We implemented a slight variation of RankJoin since we don't need joins across all 4 lists.
+\end{itemize}
 
-\begin{figure}[tb]
-  \begin{center}
-    \includegraphics[width=5in]{images/component-graph}
-  \end{center}
-  \caption{Distribution of component sizes in the citation graph}
-  \label{comp-size}
-\end{figure}
+\subsection{Tuning Parameters}
 
-\subsection{Document scores}
+To tune weights for the four factors, we obtained information about seminal papers on 6 topics from experts in the respective areas.
+We then manually picked weights that gave good results for all 6 topics.
 
-We use Apache Lucene \cite{lucene} to index documents and provide scores based
-on the content of documents. We build the usual inverted index over the corpus,
-filtering out stopwords. The structure of the documents is preserved in the XML
-corpus, so we can index titles, subtitles, abstracts, and full text as separate
-fields. We also include various metadata to simplify the implementation of the
-front-end.
+\subsection{PageRank Parameters}
+For PubCrawl's implementation of the adapted PageRank scoring function, we used several parameters for variables defined in Section \ref{sec:pagerank}:\\
 
-Lucene uses the Boolean model \cite{lancaster73} to filter documents and the
-Vector Space Model \cite{salton75} to score documents. Documents and queries
-are vectors with each term a dimension and coordinates equal to tf*idf values.
-Then, the relevance of a document to a query is related to the angle between
-them (the cosine similarity score). Lucene generalizes the cosine similarity
-score in several ways. First, documents are allowed to have multiple and
-duplicate fields. Second, Lucene allows index-time boosting of documents and
-fields as well as query-time boosting of query terms. Finally, Lucene does not
-require every term to appear in hits, instead using a coordination factor to
-score documents which contain more terms higher. These features can be
-exploited to improve the quality of search results.
+\begin{itemize}
+\item For the score source $E$, we use a uniform value.
+We minimize the value of $E$ that still results in convergence, to reduce the total amount of freely created score.
+In our system, we found $E=0.1$ to be appropriate.
 
-\subsection{Adapted PageRank}
+\item For initializing node scores, we use a linear relationship with the size of the component containing the node.
+If the total number of papers (and nodes) is $N$ and paper $p$ is in a component with $X$ nodes, then the initial score for $p$ is set to $\frac{X}{N}$.
+Thus, larger components start with initially higher scores, and typically converge with higher final scores.
 
-PageRank is a well-known algorithm for estimating the importance of a web page
-as a function of the number of incoming links \cite{brin98, page99}. It is
-plausible to extend the algorithm by analogy to academic papers and citations.
-We use the iterative algorithm as described but tune the parameters to improve
-the quality of the results for the ACM data set.
+\item For the damping factor of our final scoring function (Equation \ref{eqn:damping}), we use $d=0.85$.
+This is a reflection of the PageRank study indicating this value as reasonable, rather than a precisely chosen one.
 
-We set the score source $E$ to a uniform vector with each coordinate equal to
-$0.1$. This setting minimizes the PageRank each paper gets for free while still
-allowing the algorithm to converge. We set the damping factor $d$ to the
-suggested value of $0.85$. This setting reduces the number of iterations needed
-to converge by reducing the amount of PageRank contributed in subsequent
-iterations.
-
-We found initializing the PageRank of each paper to a constant gave suboptimal
-results because the ACM citation graph has a high number of small components.
-Papers in these components end with disproportionately high PageRank because
-further iterations do not change their initial value very much. Instead, we set
-the initial value of a paper's PageRank to the proportion of all papers
-contained in its component.
-
-\subsection{Combining document scores and PageRanks}
-
-We compute a final score used for ranking documents as a linear function of
-subscores. One issue is that these subscores are not necessarily on the same
-scale. In particular, Lucene scores are on an arbitrary scale. To address this
-issue, we normalize scores per query.
-
-The PageRank algorithm includes a normalization step at each iteration.
-However, if a particular topic is studied by only a few researchers, all the
-papers relevant to that topic will have low PageRank. To address this issue, we
-renormalize PageRanks per query.
-
-We implemented two ranking functions. The first only uses the full text score
-and PageRank. The second uses a rank join--inspired algorithm to combine lists
-of hits sorted by each of title, abstract, and full text scores and PageRank.
-Briefly, the algorithm maintains the top $k$ hits seen so far. In each
-iteration, we pop the maximum element off of the next list in round-robin order
-and hash it. When we encounter a duplicate, we update the combined score and
-its position in the top $k$. The algorithm terminates when the maximum possible
-score of unseen tuples is less than the score of the $k$th hit.
-
-To tune weights for the four factors, we obtained information about important
-papers on 6 topics from experts in the respective areas. We then manually
-picked weights that gave good results for all 6 topics.
+\end{itemize}
 
@@
 To evaluate the quality of PubCrawl results, we performed a preliminary user study.
-In this study, we compared the quality of PubCrawl results with those from Google Scholar, Microsoft Academic Search, ACM Digital Library and \citeseer.
+In this study, we compared the quality of PubCrawl results with those from Google Scholar, Microsoft Academic Search, ACM Digital Library and CiteSeer.
 
@@
 
-For 3 topics, we performed searches on Google Scholar, Microsoft Academic Search, ACM Digital Library, CiteSeer and PubCrawl.
+For 4 topics, we performed searches on Google Scholar, Microsoft Academic Search, ACM Digital Library, CiteSeer and PubCrawl.
 We then obtained lists of the top 10 ACM publication results from these search engines.
-We provided these lists to our experts.
-The experts rated each of the 10 results as Highly Relevant, Moderately Relevant and Not relevant.
+We provided these lists to our experts who rated each of the 10 results as Highly Relevant, Moderately Relevant or Not relevant.
 They also ranked the five lists in order of decreasing quality.
-Table \ref{} shows the results for the 3 test topics.
+Figure \ref{relevance1} shows the distribution of results grouped by ranks assigned by users.
+We observe that PubCrawl produces a large number of moderately relevant document while it has a low number of highly and not relevant results.
+While we would ideally like to maximize the former, the low number of non-relevant results is very important since it means that we have low false positive rate.
 
-We find that PubCrawl consistently does as well as CiteSeer and ACM DL.
+Figures \ref{relevance2} and \ref{reelvance3} show two different views of these data.
+The first plots the relevance ratio across all search engines.
+Relevance ratio is computed as (\# Highly Relevant + \# Moderately Relevant)/(\#Not Relevant).
+As we can see, PubCrawl has relevance ratio comparable to Google Scholar and Microsoft Academic Search.
+CiteSeer, on the other hand, has very poor relevance score since it produces a large number of non-relevant results.
+ACM Digital Library has the largest number of relevant documents in its results.
+
+In Figure \ref{relevance3}, we show a total quality score we define as follows: Quality Score = \# Highly Relevant Results - \# Non-relevant results + 0.1 * \# Moderately relevant results.
+We choose this metric to highly rank relevant results, penalize for non-relevant results and factor in moderately relevant results.
+
+Finally, in Figure \ref{rank1}, we show the average rank assigned to an engine based on the ranks assigned to each engine by our experts.
+A higher score (scale of 5) indicates a better rank.
+On average, PubCrawl ranked as high as the other engines except Google Scholar.
+
+\begin{figure}[t]
+\centering
+	\includegraphics[width=5in]{images/Relevance1}
+	\caption{Relevance of search results grouped as Highly Relevant, Moderately Relevant and Not Relevant.}	
+	\label{relevance1}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+	\includegraphics[width=5in]{images/Relevance2}
+	\caption{Relevance ratio vs. Search Engines.}	
+	\label{relevance2}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+	\includegraphics[width=5in]{images/Relevance3}
+	\caption{Quality Score.}	
+	\label{relevance3}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+	\includegraphics[width=5in]{images/rank}
+	\caption{Rank order of search engines (Higher score indicates better rank; scale of 5).}	
+	\label{rank1}
+\end{figure}
 
@@
 An extremely challenging question we would like to answer is what is the best way to determine appropriate weights in a ranking function.
-Using labeled data points and curve fitting or SVMs, we are likely to get a better set of results.
+Using labelled data points and curve fitting or SVMs, we are likely to get a better set of results.
 We would also like to investigate the following heuristics further: it would also be interesting to extend page rank so that it takes into account relationships between papers, i.e.
@@
 
-\section{Acknowledgments}
-
-\bibliography{refs}{}
-\bibliographystyle{acm}
+\section{Acknowledgements}
+\null
 
 \end{document}
-
-\end{document}

### 2012-05-18 report/paper.tex
Few edits to user-study and conclusion + one reference.

@@
 PubCrawl combines four scores in all - a fulltext search score, a title search score, an abstract search score and the PageRank score.
-Since Lucene does't score on a pre-defined scale, we normalize all Lucene.
-Similarly, we normalize PageRanks.
-We normalize all scores on a per-query basis.
+Since Lucene does't score on a pre-defined scale, we normalize all Lucene scores.
+Similarly, we normalize PageRanks too.
+All scores are scaled on a per-query basis instead of a per-corpus basis.
 This is particularly relevant to PageRank since results for a particular topic may all have low PageRank since the topic is studied by few researchers.
@@
 We used a simple sorting technique for this since every document returned by the search has an associated full text and page rank score.
-	\item 4-factor ranking: In order to combine multiple scores, i.e., to combine multiple sorted lists, we used the RankJoin algorithm.
+	\item 4-factor ranking: In order to combine multiple scores, i.e., to combine multiple sorted lists, we used the RankJoin algorithm \cite{DBLP:conf/vldb/IlyasAE03}.
 Briefly, RankJoin is a top-k algorithm that takes multiple sorted lists and traverses them in a round-robin fashion performing hash joins on already seen tuples.
@@
 We then manually picked weights that gave good results for all 6 topics.
+The settings we used for the user study were:  title weight (0.1), abstract weight (0), document weight (0.5), page rank (1).
 
@@
 
-Figures \ref{relevance2} and \ref{reelvance3} show two different views of these data.
+Figures \ref{relevance2} and \ref{relevance3} show two different views of these data.
 The first plots the relevance ratio across all search engines.
@@
 
-\subsection{Challenges}
-The main challenges with evaluating the user study were (1) Ground truth wasn't always clearly known, (2) Ground-truth is subjective, (3) since the data only included ACM papers, we had to discard a large number of highly relevant but non-ACM publications.
+\subsection{Discussion}
+Our preliminary user study only involved 4 topics and hence a larger study must be undertaken to rigorously study the quality of results.
+We also observed that: (1) quality of results depends heavily on the breadth of the search term (a narrow search term produces better results), (2) ground truth wasn't always clearly known, (3) ground-truth is subjective, (4) since the data only included ACM papers, we had to discard a large number of highly relevant but non-ACM publications.
+Furthermore, the lack of non-ACM paper citations causes discrepancies in our PageRank algorithm compared to other search engines.
 
-\section{Results}
-
-User study results.
-
-Some time comparisons.
+However, our preliminary user study shows that PubCrawl can find relevant documents and effectively tradeoff PageRank and text indexing scores.
 
@@
 
+In this work, we built a publication search engine based on the PageRank algorithm and the Lucene text index.
+We adapted PageRank for the specific properties of the citation graph and indexed various paper attributes such as title, abstract and full text.
+We then explored multiple ways of combining the text indexing scores with PageRank.
 We observed that it is very difficult to find a scoring function that works well for all search queries.
 We also realized that combining scores from orthogonal metrics like PageRank and text indexing may not be the best method to obtain an overall ranking.
+Our user study demonstrates that PubCrawl has a low false positive rate and produces a large number of moderately relevant results.
+However, it produces a low number of highly relevant results and there is potential to extend this work by finding better ranking functions.
 

### 2012-05-18 report/paper.tex
Incorporate Manasi's writeup about the user study

--- 2012-05-17 report/paper.tex
@@
 We implemented two ranking functions. The first only uses the full text score
-and PageRank. The second uses a rank join--inspired algorithm to combine lists
-of hits sorted by each of title, abstract, and full text scores and PageRank.
-Briefly, the algorithm maintains the top $k$ hits seen so far. In each
-iteration, we pop the maximum element off of the next list in round-robin order
-and hash it. When we encounter a duplicate, we update the combined score and
-its position in the top $k$. The algorithm terminates when the maximum possible
-score of unseen tuples is less than the score of the $k$th hit.
-
-To tune weights for the four factors, we obtained information about important
-papers on 6 topics from experts in the respective areas. We then manually
-picked weights that gave good results for all 6 topics.
+and PageRank. The second uses an algorithm based on RankJoin
+\cite{DBLP:conf/vldb/IlyasAE03} to combine lists of hits sorted by each of
+title, abstract, and full text scores and PageRank. The algorithm maintains the
+top $k$ hits seen so far. In each iteration, we pop the maximum element off of
+the next list in round-robin order and hash it. When we encounter a duplicate,
+we update the combined score and its position in the top $k$. The algorithm
+terminates when the maximum possible score of unseen tuples is less than the
+score of the $k$th hit.
 
@@
 
-To evaluate the quality of PubCrawl results, we performed a preliminary user study.
-In this study, we compared the quality of PubCrawl results with those from Google Scholar, Microsoft Academic Search, ACM Digital Library and \citeseer.
+To evaluate the quality of PubCrawl results, we performed a preliminary user
+study comparing the quality of PubCrawl results with those from Google Scholar,
+Microsoft Academic Search, ACM Digital Library and CiteSeer.
 
@@
 
-For 3 topics, we performed searches on Google Scholar, Microsoft Academic Search, ACM Digital Library, CiteSeer and PubCrawl.
-We then obtained lists of the top 10 ACM publication results from these search engines.
-We provided these lists to our experts.
-The experts rated each of the 10 results as Highly Relevant, Moderately Relevant and Not relevant.
+We obtained information about important papers on 6 topics from experts in the
+respective areas. We then manually picked weights, given in Table \ref{weights}
+that gave good results for all 6 topics.
+
+\begin{table}[bt]
+  \begin{center}
+    \begin{tabular}{ll}
+      Parameter & Weight\\
+      \hline
+      Title & 0.1\\
+      Abstract & 0\\
+      Document & 0.5\\
+      PageRank & 1\\
+    \end{tabular}
+  \end{center}
+  \caption{Manually optimized parameter settings for PubCrawl user study}
+  \label{weights}
+\end{table}
+
+For 4 topics, we performed searches on the engines, generating lists of the top
+10 ACM publications from each. We provided these lists to our experts who rated
+each of the 10 results as Highly Relevant, Moderately Relevant or Not relevant.
 They also ranked the five lists in order of decreasing quality.
-Table \ref{} shows the results for the 3 test topics.
 
-We find that PubCrawl consistently does as well as CiteSeer and ACM DL.
+Figure \ref{relevance1} shows the distribution of results grouped by ranks
+assigned by users. PubCrawl produces a large number of moderately relevant
+document but a low number both of highly relevant and not relevant results.
+While we would ideally like to maximize the former, the low number of
+irrelevant results suggests are method has a lower false positive rate.
 
-\subsection{Challenges}
-The main challenges with evaluating the user study were (1) Ground truth wasn't always clearly known, (2) Ground-truth is subjective, (3) since the data only included ACM papers, we had to discard a large number of highly relevant but non-ACM publications.
+Figures \ref{relevance2} shows the relevance ratio across all search engines.
+Relevance ratio is defined as $(H + M) / N$, where $H$ is the number of Highly
+Relevant results, $M$ is the number of Moderately Relevant results, and $N$ is
+the number of Not relevant results. PubCrawl has relevance ratio comparable to
+Google Scholar and Microsoft Academic Search. CiteSeer, on the other hand, has
+very poor relevance score since it produces a large number of irrelevant
+results. ACM Digital Library has the largest number of relevant documents in
+its results.
 
-\section{Results}
+In Figure \ref{relevance3}, we show a total quality score which we define as $H
+- N + .1 M$. We choose this metric to highly rank relevant results, penalize
+for non-relevant results and factor in moderately relevant results.
 
-User study results.
+Finally, in Figure \ref{rank1}, we show the average rank assigned to an engine
+based on the ranks assigned to each engine by our experts. A higher score
+(scale of 5) indicates a better rank. On average, PubCrawl ranked as high as
+the other engines except Google Scholar.
 
-Some time comparisons.
+\begin{figure}[p]
+\centering
+\includegraphics[width=5in]{images/Relevance1}
+\caption{Relevance of search results grouped as Highly Relevant, Moderately
+  Relevant and Not Relevant.}
+\label{relevance1}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=5in]{images/Relevance2}
+\caption{Relevance ratio vs. Search Engines.}
+\label{relevance2}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=5in]{images/Relevance3}
+\caption{Quality Score.}
+\label{relevance3}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=5in]{images/Rank}
+\caption{Rank order of search engines (Higher score indicates better rank; scale of 5).}
+\label{rank1}
+\end{figure}
+
+\subsection{Discussion}
+
+Our preliminary user study only involved 4 topics and hence a larger study must
+be undertaken to rigorously study the quality of results. We also observed
+that: (1) quality of results depends heavily on the breadth of the search term
+(a narrow search term produces better results), (2) ground truth wasn't always
+clearly known, (3) ground-truth is subjective, (4) we had to discard a large
+number of highly relevant but non-ACM publications. Furthermore, because we did
+not have data for non-ACM papers citing ACM papers, our PageRank algorithm was
+weaker compared to other search engines. However, our preliminary user study
+shows that PubCrawl can find relevant documents and effectively trade off
+PageRank and text indexing scores.
 
@@
 
-We observed that it is very difficult to find a scoring function that works well for all search queries.
-We also realized that combining scores from orthogonal metrics like PageRank and text indexing may not be the best method to obtain an overall ranking.
+In this work, we built a publication search engine based on the PageRank
+algorithm and the Lucene text index. We adapted PageRank for the specific
+properties of the citation graph and indexed various paper attributes such as
+title, abstract and full text. We then explored multiple ways of combining the
+text indexing scores with PageRank. We observed that it is very difficult to
+find a scoring function that works well for all search queries. We also
+realized that combining scores from orthogonal metrics like PageRank and text
+indexing may not be the best method to obtain an overall ranking. Our user
+study demonstrates that PubCrawl has a low false positive rate and produces a
+large number of moderately relevant results. However, it produces a low number
+of highly relevant results and there is potential to extend this work by
+finding better ranking functions.
 
-Several extensions of this work are possible.
-An extremely challenging question we would like to answer is what is the best way to determine appropriate weights in a ranking function.
-Using labeled data points and curve fitting or SVMs, we are likely to get a better set of results.
-We would also like to investigate the following heuristics further: it would also be interesting to extend page rank so that it takes into account relationships between papers, i.e.
-paper A supports paper B, paper A refutes paper B etc.
-Similarly we would like to use metadata such as paper venues in order to further refine the scoring.
-We also looked into whether we could classify papers based on the level of expertise a paper expects.
-This may also be used to boost our search results.
+We observed that it is very difficult to find a scoring function that works
+well for all search queries. We also realized that combining scores from
+orthogonal metrics like PageRank and text indexing may not be the best method
+to obtain an overall ranking.
+
+Several extensions of this work are possible. An extremely challenging question
+we would like to answer is what is the best way to determine appropriate
+weights in a ranking function. Using labeled data points and curve fitting or
+SVMs, we are likely to get a better set of results. We would also like to
+investigate the following heuristics further: it would also be interesting to
+extend page rank so that it takes into account relationships between papers,
+i.e. paper A supports paper B, paper A refutes paper B etc. Similarly we would
+like to use metadata such as paper venues in order to further refine the
+scoring. We also looked into whether we could classify papers based on the
+level of expertise a paper expects. This may also be used to boost our search
+results.
 

### 2012-05-18 report/paper.tex
Edit abstract for conciseness
Fix date
Cosmetic changes
Use a nicer font

Fix "overfull hbox" warning

Reformat some BibTeX entries
Introduce notation for containing component

@@
 Manasi Vartak (mvartak@mit.edu)}
-\date{May 16, 2012}
 
@@
 \usepackage[letterpaper,margin=1in]{geometry}
+\usepackage{palatino}
+\usepackage{mathpazo}
 
@@
 
-There are several existing search engines for academic papers, most prominently
-Google Scholar, \citeseer, and Microsoft Academic Search. Google Scholar uses a
-proprietary algorithm which combines several approaches. However, researchers
-have partially reverse engineered it \cite{beel09a, beel09b}. In particular,
-the algorithm is biased towards highly cited papers, which should highly rank
-important papers in the standard literature. However, the bias
-will also make the algorithm miss more recent influential papers. Researchers
-also uncovered several weaknesses in Google's automatic processing of documents
-which could allow authors to game search rankings \cite{beel10}.
+There are several prominent search engines for academic papers: Google Scholar,
+\citeseer, and Microsoft Academic Search. Google Scholar uses a proprietary
+algorithm which combines several approaches. However, researchers have
+partially reverse engineered it \cite{beel09a, beel09b}. In particular, the
+algorithm is biased towards highly cited papers, which should highly rank
+important papers in the standard literature. However, the bias will also make
+the algorithm miss more recent influential papers. Researchers also uncovered
+several weaknesses in Google's automatic processing of documents which could
+allow authors to game search rankings \cite{beel10}.
 
@@
   \begin{center}
-    \includegraphics[width=8in]{images/interface}
+    \includegraphics[width=\textwidth]{images/interface}
   \end{center}
@@
 \begin{equation}
-R(p)= n\left(\frac{1 - d}{N} + d\left(\sum_{c \in C}
+R(p)= n\left(\frac{1 - d}{N} + d\left(\sum_{c \in C(p)}
 \frac{R(c)}{D(c)}+E(p)\right)\right)
@@
 node, $E(\cdot)$ is the score source of a node (needed to converge with
-cycles), $d$ is the damping factor, and $n$ is the normalizing factor.
+cycles), $C(\cdot)$ is the component containing a node, $d$ is the damping
+factor, and $n$ is the normalizing factor.
 
@@
 further iterations do not change their initial value very much. Instead, we set
-the initial value of a paper's PageRank to the proportion of all papers
-contained in its component.
+the initial value of a paper's PageRank to $\vert C(p) \vert / N$ or the
+proportion of all papers contained in its component.
 
@@
 \end{document}
-
-\end{document}

### 2012-05-18 report/paper.tex
Reorganize stuff

@@
 
+\subsection{Methodology}
+
 To evaluate the quality of PubCrawl results, we performed a preliminary user
 study comparing the quality of PubCrawl results with those from Google Scholar,
-Microsoft Academic Search, ACM Digital Library and CiteSeer.
-
-\subsection{Methodology}
-
-We obtained information about important papers on 6 topics from experts in the
-respective areas. We then manually picked weights, given in Table \ref{weights}
-that gave good results for all 6 topics.
+Microsoft Academic Search, ACM Digital Library and \citeseer. We obtained
+information about important papers on 6 topics from experts in the respective
+areas. We then manually picked weights shown in Table \ref{weights} that gave
+good results for all 6 topics.
 
@@
 They also ranked the five lists in order of decreasing quality.
+
+\subsection{Results}
 

### 2012-05-18 report/paper.tex
Fix some typos

@@
 
-Figures \ref{relevance2} shows the relevance ratio across all search engines.
+Figure \ref{relevance2} shows the relevance ratio across all search engines.
 Relevance ratio is defined as $(H + M) / N$, where $H$ is the number of Highly
@@
 the number of Not relevant results. PubCrawl has relevance ratio comparable to
-Google Scholar and Microsoft Academic Search. CiteSeer, on the other hand, has
+Google Scholar and Microsoft Academic Search. \citeseer, on the other hand, has
 very poor relevance score since it produces a large number of irrelevant

### 2012-05-18 report/paper.tex
Reword for clarity/consistency

@@
 \includegraphics[width=5in]{images/Relevance1}
-\caption{Relevance of search results grouped as Highly Relevant, Moderately
-  Relevant and Not Relevant.}
+\caption{Relevance of search results across all topics}
 \label{relevance1}
@@
 \includegraphics[width=5in]{images/Relevance2}
-\caption{Relevance ratio vs. Search Engines.}
+\caption{Relevance ratio for each search engine}
 \label{relevance2}
@@
 \includegraphics[width=5in]{images/Relevance3}
-\caption{Quality Score.}
+\caption{Quality score for each search engine}
 \label{relevance3}
@@
 \includegraphics[width=5in]{images/Rank}
-\caption{Rank order of search engines (Higher score indicates better rank; scale of 5).}
+\caption{Average ranking of search engines (higher score is better)}
 \label{rank1}
@@
 not have data for non-ACM papers citing ACM papers, our PageRank algorithm was
-weaker compared to other search engines. However, our preliminary user study
-shows that PubCrawl can find relevant documents and effectively trade off
-PageRank and text indexing scores.
+weaker compared to other search engines. However, we did show that PubCrawl can
+find relevant documents and effectively trade off PageRank and text indexing
+scores.
 

### 2012-05-18 report/paper.tex
Initial acknowledgments
Merged Abhishek and Manasi's edits, moved PageRank ACM info to ACM section, formatted graph placements

--- 2012-05-18 report/paper.tex
@@
 Manasi Vartak (mvartak@mit.edu)}
+\date{May 16, 2012}
 
 \usepackage{graphicx}
-\usepackage[letterpaper,margin=1in]{geometry}
-\usepackage{palatino}
-\usepackage{mathpazo}
 
@@
 \begin{abstract}
-Searching for documents ranked by relevance is a well-studied problem in
-information retrieval. In particular, there are frameworks for estimating
-relevance as a function of the content of the document and algorithms for
-estimating relevance as a function of incoming links. However, further
-specialization of these techniques is required to search a corpus of academic
-papers. Academic papers are highly structured, lending additional weight to
-matches which appear in important sections such as the title or abstract.
-Contextual information changes the weight which should be contributed to cited
-papers. Here we describe PubCrawl, a search engine built for the ACM Digital
-Library. The system allows users to weight the relative importance of matches
-in various sections of the documents. We also implement a version of PageRank
-over the dataset. We evaluate the system in user studies.
+Searching for documents ranked by relevance is a well-studied problem for web
+pages. In particular, there are frameworks for estimating relevance as a
+function of the content of the document and algorithms for estimating relevance
+as a function of incoming links. However, further specialization of these
+techniques is required to search a corpus of academic papers. Academic papers
+are highly structured, lending additional weight to matches which appear in
+important sections such as the title or abstract. Moreover, citations have
+contextual information which changes the weight which should be contributed to
+cited papers. Here we describe PubCrawl, a search engine built for the ACM
+Digital Library. The system allows users to weight the relative importance of
+matches in various sections of the documents. We also implement a version of
+PageRank over the dataset. We evaluate the system in user studies.
 \end{abstract}
@@
 
-There are several prominent search engines for academic papers: Google Scholar,
-\citeseer, and Microsoft Academic Search. Google Scholar uses a proprietary
-algorithm which combines several approaches. However, researchers have
-partially reverse engineered it \cite{beel09a, beel09b}. In particular, the
-algorithm is biased towards highly cited papers, which should highly rank
-important papers in the standard literature. However, the bias will also make
-the algorithm miss more recent influential papers. Researchers also uncovered
-several weaknesses in Google's automatic processing of documents which could
-allow authors to game search rankings \cite{beel10}.
+There are several existing search engines for academic papers, most prominently
+Google Scholar, \citeseer, and Microsoft Academic Search. Google Scholar uses a
+proprietary algorithm which combines several approaches. However, researchers
+have partially reverse engineered it \cite{beel09a, beel09b}. In particular,
+the algorithm is biased towards highly cited papers, which should highly rank
+important papers in the standard literature. However, the bias
+will also make the algorithm miss more recent influential papers. Researchers
+also uncovered several weaknesses in Google's automatic processing of documents
+which could allow authors to game search rankings \cite{beel10}.
 
@@
 searching academic papers. The system searches over the complete ACM Digital
-Library. We use Apache Lucene to index documents and estimate relevance and
-PageRank to estimate importance. The system provides a web interface using the
-Django web framework backed by a Postgres database. Users can input queries and
-relative weights for matches in various sections of the document as well as the
-PageRank.
+Library.
+We use Apache Lucene \cite{lucene} to index documents and estimate relevance and an adapted PageRank \cite{page99} to estimate importance.
+The system provides a web interface using the Django web framework backed by a Postgres database.
+Users can input queries and relative weights for matches in various sections of the document as well as the PageRank.
 
-\section{PubCrawl Design and Implementation}
+\section{ACM Data}
+%Information about ACM data
 
-\subsection{Overview}
+The complete ACM Digital Library was obtained from the Association for Computing Machinery.
+It consists of 228,300 papers, primarily those published in ACM-affiliated venues.
+The data contains both paper text and meta-data in XML format.
 
-PubCrawl is an online search website for the ACM Digital Library built with the
-Django web framework. It is backed by a Postgres database which stores metadata
-(authors, venues, and citations) and a Lucene search index. The PubCrawl
-interface allows users to submit search terms and assign relative weights to
-title, abstract, and full text searches and PageRank. Figure \ref{interface}
-shows a screenshot of the interface.
+One important meta-data recorded is a paper's citations.
+This allows the data to form a citation graph, where papers are nodes and an edge from a paper A to a paper B indicates A cites B.
+The citation graph of the ACM data set has two interesting features that become relevant to our investigation: cycles and components.
 
-\begin{figure}[bt]
-  \begin{center}
-    \includegraphics[width=\textwidth]{images/interface}
-  \end{center}
-  \caption{PubCrawl user interface}
+In citation cycles, a paper's chain of citations returns to the paper itself.
+A number of these cycles exist in the data set, including self-citations and cycles of several papers.
+Typically, a self-citation occurs when a paper cites a different document with the same title and author but no publication information, such as a web page.
+Multi-paper cycles tend to be published around the same time.
+Often the cycle's papers are published in the same venue, making it impossible to determine a chronological ordering of the cycle.
+
+The citation graph of the ACM data is not completely connected. The graph is composed of a number of components, where papers
+in the same component are either both part of the same citation chain or share
+a common ancestor or descendant in their respective chain. This largely arises because many citation links are missing since the ACM data is limited in coverage to ACM papers. The ACM data
+exhibits 45,571 total components, with one large component of 176,285 papers,
+and a large number of smaller components ranging in size from one to ten
+papers, as displayed in Figure \ref{comp-size}.
+
+\begin{figure}[t]
+\centering \includegraphics[width=5in]{images/component-graph}
+	\caption{Sizes of components in the ACM data set and the number of each
+      size's occurrence.}
+	\label{comp-size}
+\end{figure}
+
+\section{PubCrawl Design}
+
+PubCrawl is designed to rank papers based on relevance and importance. To
+measure relevance, we use Apache Lucene, a high-performance text search engine
+library for Java \cite{lucene}. Lucene is used to provide text indexing, returning the papers
+most textually relevant to a query. To measure importance, we use a variation
+of the classic PageRank algorithm \cite{page99} on the citation graph of papers. The weighting between the text indexing and PageRank score is an input the users
+can provide, as discussed in \ref{sec:implementation}. Currently, the ACM
+dataset has been gathered and applied using PubCrawl. Through the design of the
+system, we discuss the effect of a number of its features.
+
+\subsection{Document scores}
+
+We use Apache Lucene \cite{lucene} to index documents and provide scores based
+on the content of documents. We build the usual inverted index over the corpus,
+filtering out stopwords. The structure of the documents is preserved in the XML
+corpus, so we can index titles, subtitles, abstracts, and full text as separate
+fields. We also include various metadata to simplify the implementation of the
+front-end.
+
+Lucene uses the Boolean model \cite{lancaster73} to filter documents and the
+Vector Space Model \cite{salton75} to score documents. Documents $d$ and
+queries $q$ are vectors $V(\cdot)$ with each term a dimension and coordinates
+equal to tf*idf values. Then, the relevance of a document to a query is related
+to the angle between them (the cosine similarity score). Lucene generalizes the
+cosine similarity score in several ways. First, documents are allowed to have
+multiple and duplicate fields. Second, Lucene allows index-time boosting of
+documents and fields as well as query-time boosting of query terms. Finally,
+Lucene does not require every term to appear in hits, instead using a
+coordination factor to score documents which contain more terms higher. These
+features can be exploited to improve the quality of search results.
+
+\subsection{Adapted PageRank}
+\label{sec:pagerank}
+
+The relationship between academic papers draws a strong analogy with that
+between web pages. Just as pages on the web embed links to other pages, papers
+cite other papers. This forms a directed graph of paper nodes and citation
+edges, where an edge from one paper $A$ to another paper $B$ indicates that $A$
+cited $B$.
+
+To exploit the similarity between the two environments, we use a variation of
+the PageRank algorithm \cite{page99}. PageRank is an algorithm used by the Google search engine that provides a weighted score for web pages based on the number of
+external pages that cite a particular web page, and the PageRank of those
+external pages. We use a similar framework for academic papers, where a paper's
+score is based on the number of other papers citing it, and the score of those
+papers. The most simple form of this captured by the following equation:\\
+\begin{equation}
+\label{eqn:basic}
+S(p)= \Sigma_{c \in C} \frac{S(c)}{D(c)}
+\end{equation}
+where $p$ is the paper being scored, $C$ is the set of all papers that cite
+$p$, $S$ is the scoring function, and $D$ is the degree function (indicating
+the number of papers a certain paper cites).
+
+The score of all nodes can be calculated in an iterative manner. All nodes can
+be initialized to a default score, such as 1. Then, in each round, Equation
+\ref{eqn:basic} can be applied to all nodes. This process is repeated until
+node scores converge. However, this scoring function is further complicated by
+a couple of features of academic paper relations, specifically those seen in the ACM data set: cycles and components.
+
+Citation cycles provide one source of complication.
+In general, these cycles act as a score sink, shifting the score of external nodes into the cycle round after round.
+Inside the cycle, the score rotates among nodes, preventing convergence.
+To reduce the impact of these cycles, a score source is provided for node each round, as also done in
+. To provide convergence, the total sum of all node scores must remain constant, so node scores must be normalized per round. This results in an updated scoring function of:\\
+\begin{equation}
+\label{eqn:cycle}
+S(p)= n(\Sigma_{c \in C} \frac{S(c)}{D(c)}+E(p))
+\end{equation}
+where $E$ is a source of score, $n$ is the normalization factor, and all other
+variables remain as defined.
+
+Components in the citation graph are the other source of complication. Small components are papers
+that don't cite many or any other papers in the data set and aren't heavily
+cited. This implies that nodes in small components should not be highly ranked. To adjust for this, nodes are categorized into the components they belong in.
+Instead of initializing node scores to be a constant value such as 1, they are
+instead initialized to a score linear to the size of the component containing
+the nodes. Intuitively, this means that papers in larger components will
+receive higher scores, as desired.
+
+A final variation on the basic scoring function is the incorporation of a
+damping factor $d$. A user following a citation chain will eventually stop,
+possibly at the end of the chain. Intuitively, the farther down a chain a user
+traverses, the less likely the papers will relevant and important to the
+original query, and the more likely the user will stop. The damping factor
+models this behavior by reducing the change produced by the scoring function
+as the number of rounds increases. Adapted from PageRank, this results in the
+final version of our scoring function:\\
+\begin{equation}
+\label{eqn:damping}
+S(p)= n(\frac{1-d}{N}+d(\Sigma_{c \in C} \frac{S(c)}{D(c)}+E(p)))
+\end{equation}
+where $d$ is the damping factor, $N$ is the total number of papers/nodes in the
+network, and all other variables remain as defined.
+
+\section{Implementation}
+\label{sec:implementation}
+
+%\subsection{Overview}
+PubCrawl is an online search website built with the Django web framework backed by a Postgres database and Lucene search index.
+While the Postgres database stores metadata about papers such as the citation graph, author and venue information, Lucene stores indexes for paper titles, abstracts and fulltext.
+The PubCrawl interface allows users to submit search terms and relative weights to be assigned to title, abstract, full text searches and PageRank.
+Figure \ref{interface} shows a screenshot of the interface.
+
+\begin{figure}[t]
+\centering
+	\includegraphics[width=8in]{images/interface}
+	\caption{PubCrawl interface allowing search term and relative weight inputs.}	
 	\label{interface}
@@
 
-\subsection{ACM Digital Library}
+\subsection{Scores and Scaling}
+PubCrawl combines four scores in all - a fulltext search score, a title search score, an abstract search score and the PageRank score.
+Since Lucene does't score on a pre-defined scale, we normalize all Lucene scores.
+Similarly, we normalize PageRanks too.
+All scores are scaled on a per-query basis instead of a per-corpus basis.
+This is particularly relevant to PageRank since results for a particular topic may all have low PageRank since the topic is studied by few researchers.
+By normalizing per-query, we do not penalize topics with a small number of papers.
 
-The ACM Digital Library is a corpus of over 223,800 academic papers published
-in ACM journals or conference proceedings. The data set is in XML format with
-rich metadata including citations. Unlike \citeseer, we do not have to do
-sophisticated NLP to build a citation graph, increasing the quality of the
-resulting graph.
+\subsection{Ranking}
+An important challenge faced by PubCrawl is how to effectively combine the four scores above to get an over quality score for a document.
+We implemented two types of simple ranking functions for this purpose:
 
-However, because the data set is limited to ACM publications, the citation
-graph is highly disconnected. Although the vast majority of the papers
-(176,285) are contained in one component, in total there are 45,571 connected
-components. Figure \ref{comp-size} shows the size distribution of these
-components is heavily skewed. We take special consideration of component size
-in our adaptation of the PageRank algorithm.
+\begin{itemize}
+	\item 2-factor ranking: As a first step, we only allowed full text and page rank scores to be combined.
+We used a simple sorting technique for this since every document returned by the search has an associated full text and page rank score.
+	\item 4-factor ranking: In order to combine multiple scores, i.e., to combine multiple sorted lists, we used the RankJoin algorithm \cite{DBLP:conf/vldb/IlyasAE03}.
+Briefly, RankJoin is a top-k algorithm that takes multiple sorted lists and traverses them in a round-robin fashion performing hash joins on already seen tuples.
+It is able to stop before traversing all tuples because once the max possible score of unseen tuples becomes lesser than the minimum score of the top-k tuples, we are guaranteed to have the required top-k set of tuples.
+We implemented a slight variation of RankJoin since we don't need joins across all 4 lists.
+\end{itemize}
 
-\begin{figure}[tb]
-  \begin{center}
-    \includegraphics[width=5in]{images/component-graph}
-  \end{center}
-  \caption{Distribution of component sizes in the citation graph}
-  \label{comp-size}
-\end{figure}
+\subsection{Tuning Parameters}
 
-\subsection{Document scores}
+To tune weights for the four factors, we obtained information about seminal papers on 6 topics from experts in the respective areas.
+We then manually picked weights that gave good results for all 6 topics.
+The settings we used for the user study were:  title weight (0.1), abstract weight (0), document weight (0.5), page rank (1).
 
-We use Apache Lucene \cite{lucene} to index documents and compute relevance
-scores. We build the usual inverted index over the corpus, filtering out
-stopwords. The structure of the documents is preserved in the XML corpus, so we
-can easily parse titles, subtitles, abstracts, and full text. Lucene supports
-multi-field documents, so we index and perform searches on each independently.
-We also include various metadata to simplify the implementation of the
-front-end.
+\subsection{PageRank Parameters}
+For PubCrawl's implementation of the adapted PageRank scoring function, we used several parameters for variables defined in Section \ref{sec:pagerank}:\\
 
-Lucene uses the Boolean model \cite{lancaster73} to filter documents and the
-Vector Space Model \cite{salton75} to score documents. Documents and queries
-are vectors with each term a dimension and coordinates equal to tf*idf values.
-Then, the relevance of a document to a query is related to the angle between
-them (the cosine similarity score). Lucene generalizes the cosine similarity
-score in several ways. First, documents are allowed to have multiple and
-duplicate fields. Second, Lucene allows index-time boosting of documents and
-fields as well as query-time boosting of query terms. Finally, Lucene does not
-require every term to appear in hits, instead using a coordination factor to
-score documents which contain more terms higher.
+\begin{itemize}
+\item For the score source $E$, we use a uniform value.
+We minimize the value of $E$ that still results in convergence, to reduce the total amount of freely created score.
+In our system, we found $E=0.1$ to be appropriate.
 
-While these features can be exploited to improve the quality of search results,
-they also have some unintended side effects. In particular, Lucene's scoring is
-biased towards matches in shorter fields due to the way it normalizes even
-though fields are boosted equally by default. We investigated using user
-inputted weights to boost individual fields within Lucene's scoring mechanism,
-but found it as difficult to combine the resulting scores with PageRank as
-performing three separate searches and combining four scores.
+\item For initializing node scores, we use a linear relationship with the size of the component containing the node.
+If the total number of papers (and nodes) is $N$ and paper $p$ is in a component with $X$ nodes, then the initial score for $p$ is set to $\frac{X}{N}$.
+Thus, larger components start with initially higher scores, and typically converge with higher final scores.
 
-\subsection{Adapted PageRank}
+\item For the damping factor of our final scoring function (Equation \ref{eqn:damping}), we use $d=0.85$.
+This is a reflection of the PageRank study \cite{page99} indicating this value as reasonable, rather than a precisely chosen one.
 
-PageRank is a well-known algorithm for estimating the importance of a web page
-as a function of the number of incoming links \cite{brin98, page99}. It is
-plausible to extend the algorithm by analogy to academic papers and citations.
-We use the iterative algorithm as described but tune the parameters to improve
-the quality of the results for the ACM data set. The update rule is:
-
-\begin{equation}
-R(p)= n\left(\frac{1 - d}{N} + d\left(\sum_{c \in C(p)}
-\frac{R(c)}{D(c)}+E(p)\right)\right)
-\end{equation}
-
-where $R(\cdot)$ is the PageRank of a node, $D(\cdot)$ is the outdegree of a
-node, $E(\cdot)$ is the score source of a node (needed to converge with
-cycles), $C(\cdot)$ is the component containing a node, $d$ is the damping
-factor, and $n$ is the normalizing factor.
-
-We set $E$ to a uniform vector with each coordinate equal to $0.1$. This
-setting minimizes the PageRank each paper gets for free while still allowing
-the algorithm to converge. We set $d$ to the suggested value of $0.85$. This
-setting reduces the number of iterations needed to converge by reducing the
-amount of PageRank contributed in subsequent iterations.
-
-We found initializing the PageRank of each paper to a constant gave suboptimal
-results because the ACM citation graph has a high number of small components.
-Papers in these components end with disproportionately high PageRank because
-further iterations do not change their initial value very much. Instead, we set
-the initial value of a paper's PageRank to $\vert C(p) \vert / N$ or the
-proportion of all papers contained in its component.
-
-\subsection{Combining document scores and PageRanks}
-
-We compute a final score used for ranking documents as a linear function of
-subscores. One issue is that these subscores are not necessarily on the same
-scale. In particular, Lucene scores are on an arbitrary scale. To address this
-issue, we normalize scores per query.
-
-The PageRank algorithm includes a normalization step at each iteration.
-However, if a particular topic is studied by only a few researchers, all the
-papers relevant to that topic will have low PageRank. To address this issue, we
-renormalize PageRanks per query.
-
-We implemented two ranking functions. The first only uses the full text score
-and PageRank. The second uses an algorithm based on RankJoin
-\cite{DBLP:conf/vldb/IlyasAE03} to combine lists of hits sorted by each of
-title, abstract, and full text scores and PageRank. The algorithm maintains the
-top $k$ hits seen so far. In each iteration, we pop the maximum element off of
-the next list in round-robin order and hash it. When we encounter a duplicate,
-we update the combined score and its position in the top $k$. The algorithm
-terminates when the maximum possible score of unseen tuples is less than the
-score of the $k$th hit.
+\end{itemize}
 
@@
 
-\subsection{Methodology}
+To evaluate the quality of PubCrawl results, we performed a preliminary user study.
+In this study, we compared the quality of PubCrawl results with those from Google Scholar, Microsoft Academic Search, ACM Digital Library and CiteSeer.
 
-To evaluate the quality of PubCrawl results, we performed a preliminary user
-study comparing the quality of PubCrawl results with those from Google Scholar,
-Microsoft Academic Search, ACM Digital Library and \citeseer. We obtained
-information about important papers on 6 topics from experts in the respective
-areas. We then manually picked weights shown in Table \ref{weights} that gave
-good results for all 6 topics.
-
-\begin{table}[bt]
-  \begin{center}
-    \begin{tabular}{ll}
-      Parameter & Weight\\
-      \hline
-      Title & 0.1\\
-      Abstract & 0\\
-      Document & 0.5\\
-      PageRank & 1\\
-    \end{tabular}
-  \end{center}
-  \caption{Manually optimized parameter settings for PubCrawl user study}
-  \label{weights}
-\end{table}
-
-For 4 topics, we performed searches on the engines, generating lists of the top
-10 ACM publications from each. We provided these lists to our experts who rated
-each of the 10 results as Highly Relevant, Moderately Relevant or Not relevant.
-They also ranked the five lists in order of decreasing quality.
-
-\subsection{Results}
-
-Figure \ref{relevance1} shows the distribution of results grouped by ranks
-assigned by users. PubCrawl produces a large number of moderately relevant
-document but a low number both of highly relevant and not relevant results.
-While we would ideally like to maximize the former, the low number of
-irrelevant results suggests are method has a lower false positive rate.
-
-Figure \ref{relevance2} shows the relevance ratio across all search engines.
-Relevance ratio is defined as $(H + M) / N$, where $H$ is the number of Highly
-Relevant results, $M$ is the number of Moderately Relevant results, and $N$ is
-the number of Not relevant results. PubCrawl has relevance ratio comparable to
-Google Scholar and Microsoft Academic Search. \citeseer, on the other hand, has
-very poor relevance score since it produces a large number of irrelevant
-results. ACM Digital Library has the largest number of relevant documents in
-its results.
-
-In Figure \ref{relevance3}, we show a total quality score which we define as $H
-- N + .1 M$. We choose this metric to highly rank relevant results, penalize
-for non-relevant results and factor in moderately relevant results.
-
-Finally, in Figure \ref{rank1}, we show the average rank assigned to an engine
-based on the ranks assigned to each engine by our experts. A higher score
-(scale of 5) indicates a better rank. On average, PubCrawl ranked as high as
-the other engines except Google Scholar.
-
-\begin{figure}[p]
+\begin{figure}[t]
 \centering
 	\includegraphics[width=5in]{images/Relevance1}
-\caption{Relevance of search results grouped as Highly Relevant, Moderately
-  Relevant and Not Relevant.}
+	\caption{Relevance of search results grouped as Highly Relevant, Moderately Relevant and Not Relevant.}	
 	\label{relevance1}
@@
 
-\begin{figure}[p]
+\subsection{Methodology}
+
+For 4 topics, we performed searches on Google Scholar, Microsoft Academic Search, ACM Digital Library, CiteSeer and PubCrawl.
+We then obtained lists of the top 10 ACM publication results from these search engines.
+We provided these lists to our experts who rated each of the 10 results as Highly Relevant, Moderately Relevant or Not relevant.
+They also ranked the five lists in order of decreasing quality.
+Figure \ref{relevance1} shows the distribution of results grouped by ranks assigned by users.
+We observe that PubCrawl produces a large number of moderately relevant document while it has a low number of highly and not relevant results.
+While we would ideally like to maximize the former, the low number of non-relevant results is very important since it means that we have low false positive rate.
+
+\newpage
+
+\begin{figure}[t]
 \centering
@@
 
-\begin{figure}[p]
+\begin{figure}[!ht]
 \centering
@@
 
-\begin{figure}[p]
+\newpage
+
+Figures \ref{relevance2} and \ref{relevance3} show two different views of these data.
+The first plots the relevance ratio across all search engines.
+Relevance ratio is computed as (\# Highly Relevant + \# Moderately Relevant)/(\#Not Relevant).
+As we can see, PubCrawl has relevance ratio comparable to Google Scholar and Microsoft Academic Search.
+CiteSeer, on the other hand, has very poor relevance score since it produces a large number of non-relevant results.
+ACM Digital Library has the largest number of relevant documents in its results.
+
+In Figure \ref{relevance3}, we show a total quality score we define as follows: Quality Score = \# Highly Relevant Results - \# Non-relevant results + 0.1 * \# Moderately relevant results.
+We choose this metric to highly rank relevant results, penalize for non-relevant results and factor in moderately relevant results.
+
+Finally, in Figure \ref{rank1}, we show the average rank assigned to an engine based on the ranks assigned to each engine by our experts.
+A higher score (scale of 5) indicates a better rank.
+On average, PubCrawl ranked as high as the other engines except Google Scholar.
+
+\begin{figure}[!h]
 \centering
-\includegraphics[width=5in]{images/Rank}
+	\includegraphics[width=5in]{images/rank}
 	\caption{Rank order of search engines (Higher score indicates better rank; scale of 5).}	
@@
 \subsection{Discussion}
+Our preliminary user study only involved 4 topics and hence a larger study must be undertaken to rigorously study the quality of results.
+We also observed that: (1) quality of results depends heavily on the breadth of the search term (a narrow search term produces better results), (2) ground truth wasn't always clearly known, (3) ground-truth is subjective, (4) since the data only included ACM papers, we had to discard a large number of highly relevant but non-ACM publications.
+Furthermore, the lack of non-ACM paper citations causes discrepancies in our PageRank algorithm compared to other search engines.
 
-Our preliminary user study only involved 4 topics and hence a larger study must
-be undertaken to rigorously study the quality of results. We also observed
-that: (1) quality of results depends heavily on the breadth of the search term
-(a narrow search term produces better results), (2) ground truth wasn't always
-clearly known, (3) ground-truth is subjective, (4) we had to discard a large
-number of highly relevant but non-ACM publications. Furthermore, because we did
-not have data for non-ACM papers citing ACM papers, our PageRank algorithm was
-weaker compared to other search engines. However, our preliminary user study
-shows that PubCrawl can find relevant documents and effectively trade off
-PageRank and text indexing scores.
+However, our preliminary user study shows that PubCrawl can find relevant documents and effectively tradeoff PageRank and text indexing scores.
 
@@
 
-In this work, we built a publication search engine based on the PageRank
-algorithm and the Lucene text index. We adapted PageRank for the specific
-properties of the citation graph and indexed various paper attributes such as
-title, abstract and full text. We then explored multiple ways of combining the
-text indexing scores with PageRank. We observed that it is very difficult to
-find a scoring function that works well for all search queries. We also
-realized that combining scores from orthogonal metrics like PageRank and text
-indexing may not be the best method to obtain an overall ranking. Our user
-study demonstrates that PubCrawl has a low false positive rate and produces a
-large number of moderately relevant results. However, it produces a low number
-of highly relevant results and there is potential to extend this work by
-finding better ranking functions.
+In this work, we built a publication search engine based on the PageRank algorithm and the Lucene text index.
+We adapted PageRank for the specific properties of the citation graph and indexed various paper attributes such as title, abstract and full text.
+We then explored multiple ways of combining the text indexing scores with PageRank.
+We observed that it is very difficult to find a scoring function that works well for all search queries.
+We also realized that combining scores from orthogonal metrics like PageRank and text indexing may not be the best method to obtain an overall ranking.
+Our user study demonstrates that PubCrawl has a low false positive rate and produces a large number of moderately relevant results.
+However, it produces a low number of highly relevant results and there is potential to extend this work by finding better ranking functions.
 
-We observed that it is very difficult to find a scoring function that works
-well for all search queries. We also realized that combining scores from
-orthogonal metrics like PageRank and text indexing may not be the best method
-to obtain an overall ranking.
-
-Several extensions of this work are possible. An extremely challenging question
-we would like to answer is what is the best way to determine appropriate
-weights in a ranking function. Using labeled data points and curve fitting or
-SVMs, we are likely to get a better set of results. We would also like to
-investigate the following heuristics further: it would also be interesting to
-extend page rank so that it takes into account relationships between papers,
-i.e. paper A supports paper B, paper A refutes paper B etc. Similarly we would
-like to use metadata such as paper venues in order to further refine the
-scoring. We also looked into whether we could classify papers based on the
-level of expertise a paper expects. This may also be used to boost our search
-results.
+Several extensions of this work are possible.
+An extremely challenging question we would like to answer is what is the best way to determine appropriate weights in a ranking function.
+Using labelled data points and curve fitting or SVMs, we are likely to get a better set of results.
+We would also like to investigate the following heuristics further: it would also be interesting to extend page rank so that it takes into account relationships between papers, i.e.
+paper A supports paper B, paper A refutes paper B etc.
+Similarly we would like to use metadata such as paper venues in order to further refine the scoring.
+We also looked into whether we could classify papers based on the level of expertise a paper expects.
+This may also be used to boost our search results.
 
 \section{Acknowledgments}
+We'd like to thank Samuel Madden, Adam Marcus, and Eugene Wu for their help during this project. They provided insightful observations and guidance throughout.
 

### 2012-05-18 report/paper.tex
Define N in the equation

--- 2012-05-18 report/paper.tex
@@
 node, $E(\cdot)$ is the score source of a node (needed to converge with
-cycles), $C(\cdot)$ is the component containing a node, $d$ is the damping
-factor, and $n$ is the normalizing factor.
+cycles), $C(\cdot)$ is the component containing a node, $N$ is the total number
+of papers, $d$ is the damping factor, and $n$ is a normalizing factor.
 
@@
 
+We acknowledge Adam Marcus and Eugene Wu for their assistance with the user
+studies.
+
 \bibliography{refs}{}

### 2012-05-18 report/paper.tex
Add link to the system

@@
 \documentclass[12pt]{article}
+\usepackage{hyperref}
 \setcounter{secnumdepth}{2} 
@@
 papers. Here we describe PubCrawl, a search engine built for the ACM Digital
-Library. The system allows users to weight the relative importance of matches
-in various sections of the documents. We also implement a version of PageRank
-over the dataset. We evaluate the system in user studies.
+Library available at \url{http://saw.csail.mit.edu:9000}. The system allows
+users to weight the relative importance of matches in various sections of the
+documents. We also implement a version of PageRank over the dataset. We
+evaluate the system in user studies and find it produces comparable results to
+other search engines.
 \end{abstract}
@@
 
-Here, we present PubCrawl, a system built to test ranking algorithms for
-searching academic papers. The system searches over the complete ACM Digital
-Library. We use Apache Lucene to index documents and estimate relevance and
-PageRank to estimate importance. The system provides a web interface using the
-Django web framework backed by a Postgres database. Users can input queries and
-relative weights for matches in various sections of the document as well as the
-PageRank.
-
 \section{PubCrawl Design and Implementation}
@@
 
-PubCrawl is an online search website for the ACM Digital Library built with the
-Django web framework. It is backed by a Postgres database which stores metadata
-(authors, venues, and citations) and a Lucene search index. The PubCrawl
-interface allows users to submit search terms and assign relative weights to
-title, abstract, and full text searches and PageRank. Figure \ref{interface}
-shows a screenshot of the interface.
+Here, we present PubCrawl, a new search engine for the ACM Digital Library
+available at \url{http://saw.csail.mit.edu:9000}. The PubCrawl interface allows
+users to submit search terms and assign relative weights to title, abstract,
+and full text searches and PageRank. It uses the Django web framework for the
+front-end interface and is backed by a Postgres database which stores metadata
+(authors, venues, and citations) and a Lucene search index. Figure
+\ref{interface} shows a screenshot of the interface.
 
-\begin{figure}[bt]
+\begin{figure}[p]
   \begin{center}
@@
 components is heavily skewed. We take special consideration of component size
-in our adaptation of the PageRank algorithm.
+in our adaptation of the PageRank algorithm. Figure \ref{degree-dist} shows the
+distribution of outdegrees in the largest component of the citation graph. As
+expected, this distribution follows a power law.
 
-\begin{figure}[tb]
+\begin{figure}[p]
   \begin{center}
@@
   \label{comp-size}
+\end{figure}
+
+\begin{figure}[p]
+  \begin{center}
+    \includegraphics{images/degree-graph}
+  \end{center}
+  \caption{Distribution of outdegrees in the largest component of the citation
+    graph}
+  \label{degree-dist}
 \end{figure}
@@
 
+Figure \ref{pagerank-dist} shows the distribution of PageRanks computed in that
+component. This distribution also follows a power law, which is expected given
+the distribution of outdegrees.
+
+\begin{figure}[p]
+  \begin{center}
+    \includegraphics{images/pageranks}
+  \end{center}
+  \caption{Distribution of PageRanks in the largest component of the citation
+    graph}
+  \label{pagerank-dist}
+\end{figure}
+
 \subsection{Combining document scores and PageRanks}
@@
 top $k$ hits seen so far. In each iteration, we pop the maximum element off of
-the next list in round-robin order and hash it. When we encounter a duplicate,
-we update the combined score and its position in the top $k$. The algorithm
-terminates when the maximum possible score of unseen tuples is less than the
-score of the $k$th hit.
+the next list in round-robin order and hash it. If the element can be joined
+with an element seen from each of the other lists, then we update its score in
+the top $k$. We special case the list of abstract scores because not all
+documents have abstracts. The algorithm terminates when the maximum possible
+score of unseen tuples is less than the score of the $k$th hit.
 
@@
 Microsoft Academic Search, ACM Digital Library and \citeseer. We obtained
-information about important papers on 6 topics from experts in the respective
-areas. We then manually picked weights shown in Table \ref{weights} that gave
-good results for all 6 topics.
+information from experts about important papers on 6 topics: Provenance, stream
+processing, Twitter, crowdsourcing, parallel databases, and NoSQL. We then
+manually picked weights shown in Table \ref{weights} that gave good results for
+all 6 topics.
 
-\begin{table}[bt]
+\begin{table}[p]
   \begin{center}
@@
       Title & 0.1\\
-      Abstract & 0\\
+      Abstract & 0.01\\
       Document & 0.5\\
@@
 
-For 4 topics, we performed searches on the engines, generating lists of the top
-10 ACM publications from each. We provided these lists to our experts who rated
+For the user study, we threw out Provenance and NoSQL from the topics list.
+Provenance did not have enough papers in the ACM data set; NoSQL is not a
+commonly used term even in papers about such systems. For the remaining topics,
+we performed searches on each of the engines, generating lists of the top 10
+ACM publications from each. We provided these lists to our experts who rated
 each of the 10 results as Highly Relevant, Moderately Relevant or Not relevant.
@@
 
-Figure \ref{relevance1} shows the distribution of results grouped by ranks
-assigned by users. PubCrawl produces a large number of moderately relevant
-document but a low number both of highly relevant and not relevant results.
-While we would ideally like to maximize the former, the low number of
-irrelevant results suggests are method has a lower false positive rate.
+Table \ref{ratios} shows the distribution of relevance of results for each
+search engine. Relevant results include both moderately and highly relevant
+results. PubCrawl produces a comparable number of relevant documents to the
+other search engines. We note \citeseer\ produces a large fraction of
+irrelevant documents, which we suspect is due to its noisy data set.
 
-Figure \ref{relevance2} shows the relevance ratio across all search engines.
-Relevance ratio is defined as $(H + M) / N$, where $H$ is the number of Highly
-Relevant results, $M$ is the number of Moderately Relevant results, and $N$ is
-the number of Not relevant results. PubCrawl has relevance ratio comparable to
-Google Scholar and Microsoft Academic Search. \citeseer, on the other hand, has
-very poor relevance score since it produces a large number of irrelevant
-results. ACM Digital Library has the largest number of relevant documents in
-its results.
+However, PubCrawl produces a relatively low number of highly relevant results.
+We believe there are several reasons this is the case. First, our citation
+graph does not include non-ACM papers. This means relevant papers may not
+necessarily have high PageRank in our system. Second, our Lucene text index
+does not index $n$-grams, which reduces the quality of results for multiword
+queries. Third, the Lucene scoring function based on VSM has been superseded by
+other information retrieval metrics.
 
-In Figure \ref{relevance3}, we show a total quality score which we define as $H
-- N + .1 M$. We choose this metric to highly rank relevant results, penalize
-for non-relevant results and factor in moderately relevant results.
+Figure \ref{relevance3} shows a quality score for each search engine, defined
+as $H - N + .1 M$, where $H$ is the number of Highly Relevant papers, $M$ is
+the number of Moderately Relevant papers, and $N$ is the number of Not Relevant
+papers.
 
-Finally, in Figure \ref{rank1}, we show the average rank assigned to an engine
-based on the ranks assigned to each engine by our experts. A higher score
-(scale of 5) indicates a better rank. On average, PubCrawl ranked as high as
-the other engines except Google Scholar.
+Figure \ref{rank1} shows the average rank assigned to an engine based on the
+ranks assigned to each engine by our experts. A higher score (scale of 5)
+indicates a better rank. On average, PubCrawl ranked as high as the other
+engines except Google Scholar.
 
-\begin{figure}[p]
-\centering
-\includegraphics[width=5in]{images/Relevance1}
-\caption{Relevance of search results across all topics}
-\label{relevance1}
-\end{figure}
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=5in]{images/Relevance2}
-\caption{Relevance ratio for each search engine}
-\label{relevance2}
-\end{figure}
+\begin{table}[p]
+  \begin{center}
+    \begin{tabular}{llll}
+      Search Engine & Relevant & Highly Relevant & Not Relevant\\
+      \hline
+      Google Scholar & 0.9 & 0.45 & 0.1 \\
+      Microsoft Academic Search & 0.875 & 0.275 & 0.125 \\
+      \citeseer & 0.6 & 0.125 & 0.4 \\
+      ACM Digital Library & 0.975 & 0.125 & 0.025 \\
+      PubCrawl & 0.95 & 0.1 & 0.075 \\
+    \end{tabular}
+  \end{center}
+  \caption{Ratio of results in each relevance category by search engine}
+  \label{ratios}
+\end{table}
 
@@
 
-\subsection{Discussion}
-
 Our preliminary user study only involved 4 topics and hence a larger study must
@@
 that: (1) quality of results depends heavily on the breadth of the search term
-(a narrow search term produces better results), (2) ground truth wasn't always
+(a narrow search term produces better results), (2) ground truth was not always
 clearly known, (3) ground-truth is subjective, (4) we had to discard a large
@@
 
-We acknowledge Adam Marcus and Eugene Wu for their assistance with the user
-studies.
+We acknowledge James Cowling, Adam Marcus, Eugene Wu for their assistance with
+the user studies and Sam Madden for his feedback on our methods.
 

### 2012-05-18 report/paper.tex
Remove redundant exposition

--- 2012-05-18 report/paper.tex
@@
 features, and shows the same weakness to ranking optimization as Scholar.
-
-Here, we present PubCrawl, a system built to test ranking algorithms for
-searching academic papers. The system searches over the complete ACM Digital
-Library. We use Apache Lucene to index documents and estimate relevance and
-PageRank to estimate importance. The system provides a web interface using the
-Django web framework backed by a Postgres database. Users can input queries and
-relative weights for matches in various sections of the document as well as the
-PageRank.
 

### 2012-05-18 report/paper.tex
Add more statistics about the citation graph
Outdegree distribution and PageRank distribution

@@
 proportion of all papers contained in its component.
+
+Figure \ref{pagerank-dist} shows the distribution of PageRanks computed in that
+component. This distribution also follows a power law, which is expected given
+the distribution of outdegrees.
+
+\begin{figure}[p]
+  \begin{center}
+    \includegraphics{images/pageranks}
+  \end{center}
+  \caption{Distribution of PageRanks in the largest component of the citation
+    graph}
+  \label{pagerank-dist}
+\end{figure}
 

### 2012-05-18 report/paper.tex
Fix description of RankJoin
More information about user study

--- 2012-05-18 report/paper.tex
@@
 \documentclass[12pt]{article}
-\usepackage{hyperref}
 \setcounter{secnumdepth}{2} 
@@
 papers. Here we describe PubCrawl, a search engine built for the ACM Digital
-Library available at \url{http://saw.csail.mit.edu:9000}. The system allows
-users to weight the relative importance of matches in various sections of the
-documents. We also implement a version of PageRank over the dataset. We
-evaluate the system in user studies and find it produces comparable results to
-other search engines.
+Library. The system allows users to weight the relative importance of matches
+in various sections of the documents. We also implement a version of PageRank
+over the dataset. We evaluate the system in user studies.
 \end{abstract}
@@
 
-Here, we present PubCrawl, a new search engine for the ACM Digital Library
-available at \url{http://saw.csail.mit.edu:9000}. The PubCrawl interface allows
-users to submit search terms and assign relative weights to title, abstract,
-and full text searches and PageRank. It uses the Django web framework for the
-front-end interface and is backed by a Postgres database which stores metadata
-(authors, venues, and citations) and a Lucene search index. Figure
-\ref{interface} shows a screenshot of the interface.
+PubCrawl is an online search website for the ACM Digital Library built with the
+Django web framework. It is backed by a Postgres database which stores metadata
+(authors, venues, and citations) and a Lucene search index. The PubCrawl
+interface allows users to submit search terms and assign relative weights to
+title, abstract, and full text searches and PageRank. Figure \ref{interface}
+shows a screenshot of the interface.
 
-\begin{figure}[p]
+\begin{figure}[bt]
   \begin{center}
@@
 
-We acknowledge James Cowling, Adam Marcus, Eugene Wu for their assistance with
-the user studies and Sam Madden for his feedback on our methods.
+We acknowledge Adam Marcus and Eugene Wu for their assistance with the user
+studies.
 
